### 2022-04-15 1_page_request.tex
First commit, request finished, paper not began

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Proposition of New Experiment to Better Understand the Relation Between Typicality and Prototypes%\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Samuel Kostadinov}
%\IEEEauthorblockA{\textit{Department of } \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
}

\maketitle

\section{Introduction}
In this paper, I would like to propose an experiment to gain higher knowledge about the bound between typicality and key features of an object. 
The first step of the experiment is to extract the key features of an image. 
After extracting the features, we build a prototype of the image. 
As the last step, through a siamese network, we evaluate the similarity of an image. 
This process can help us understand if there is a bond between the typicality and resemblance to a prototype.

\section{The experiment}
The experiment I would like to suggest is composed of some phases. The first thing to do is to collect the images for the experiment. 
The collected images should be part of different categories like, for example, "birds" or "dogs". 
Then there is data collection about human typicality judgments. To do this, there should be a survey in which users rate the typicality of the previously collected images. 
Once the data are complete, in order to reduce possible noise, we should average the data.  
While collecting the data, there is the possibility to start working on the images. 
The first step is to extract meaningful features. 
Some techniques that range from simple edge detection to deformable shape analysis may be functional.
Other strategies that require the presence of neural networks, either fully connected or convolutional, are used in medical imaging and can be useful if adapted to a non-medical domain. 
Moreover, if the dataset contains hyperspectral images, some specific techniques that use convolutional or recurrent neural networks can be used to extract meaningful features. 
The following step is to build a prototype image based on the features extracted.
After building the prototype, the following step is to train a deep learning siamese network that will give a similarity estimation. 
This kind of network gives a similarity measure between two inputs. 
A siamese network's training requires a loss function that measures the distance between the two examples fed to the network. 
This can be helpful since if we use a custom loss function, defined based on human typicality rates, we can have an estimation on how similar is an image to the prototype that humans have. 
Moreover, if a different loss function is used, there is the possibility to understand how similar are the neural network's and the human's similarity concepts.

\section*{Some references}

\begin{itemize}

	\item Edge extraction methods \cite{b1}
	\item Shape correspondence \cite{b2}, \cite{b3}
	\item Medical imaging feature extraction \cite{b4}
	\item CNN feature extraction for pneumonia \cite{b5}
	\item Hybrid feature extraction for brain tumour classification \cite{b6}
	\item Hyperspectral feature extraction methods \cite {b7}
	%\item Siamese Networoks \cite{b8}
	\item Learning similarity metric for face verification \cite{b8}
	\item Learning similarity metrics (Cutting-Edge Trends in Deep Learning and Recognition course, University of Ilinois) \cite{b9}
	\item Understanding the contrastive loss reference \cite{b9}

\end{itemize}

\begin{thebibliography}{00}

\bibitem{b1} Owotogbe, JS and Ibiyemi, TS and Adu, BA, ``Edge detection techniques on digital images-a review'', Int J Innov Sci Res Technol, vol 2, pp. 329--332, 2019
\bibitem{b2}Sahillioğlu, Y. Recent advances in shape correspondence. Vis Comput 36, 1705–1721 (2020). https://doi.org/10.1007/s00371-019-01760-0
\bibitem{b3} Halimi, Oshri and Litany, Or and Rodola, Emanuele and Bronstein, Alex M and Kimmel, Ron, ``Unsupervised learning of dense shape correspondence'', Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition, pp. 4370--4379, 2019
\bibitem{b4} Chiranji Lal Chowdhary, D.P. Acharjya, ``Segmentation and Feature Extraction in Medical Imaging: A Systematic Review, Procedia Computer Science'', vol. 167, pp. 26-36, 2020, ISSN 1877-0509, https://doi.org/10.1016/j.procs.2020.03.179
\bibitem{b5} Varshni, Dimpy and Thakral, Kartik and Agarwal, Lucky and Nijhawan, Rahul and Mittal, Ankush, ``Pneumonia detection using CNN based feature extraction'', 2019 IEEE international conference on electrical, computer and communication technologies (ICECCT), pp. 1--7, 2019
\bibitem{b6} Gumaei, Abdu and Hassan, Mohammad Mehedi and Hassan, Md Rafiul and Alelaiwi, Abdulhameed and Fortino, Giancarlo, ``A hybrid feature extraction method with regularized extreme learning machine for brain tumor classification'', IEEE Access, vol. 7, pp. 36266--36273, 2019
\bibitem{b7} B. Rasti et al., "Feature Extraction for Hyperspectral Imagery: The Evolution From Shallow to Deep: Overview and Toolbox," in IEEE Geoscience and Remote Sensing Magazine, vol. 8, no. 4, pp. 60-88, Dec. 2020, doi: 10.1109/MGRS.2020.2979764
%\bibitem{b8} https://en.wikipedia.org/wiki/Siamese_neural_network
\bibitem{b8} Chopra, S.; Hadsell, R.; LeCun, Y., ``Learning a similarity metric discriminatively, with application to face verification'', 2005 IEEE Computer Society Conference on Computer Vision and Pattern Recognition, vol.1, pp. 539–546, doi:10.1109/CVPR.2005.202, 
\bibitem{b9} Chatterjee, Moitreya; Luo, Yunan, Similarity Learning with (or without) Convolutional Neural Network, 2017
\bibitem{b9} Wang, Feng and Liu, Huaping, ``Understanding the behaviour of contrastive loss'', Proceedings of the IEEE/CVF conference on computer vision and pattern recognition, pp. 2495--2504, 2021

%\bibitem{b10} Wang, Feng and Liu, Huaping; ``Understanding the behaviour of contrastive loss''; Proceedings of the IEEE/CVF conference on computer vision and pattern recognition; pp. 2495--2504, 2021

\end{thebibliography}
\vspace{12pt}

\end{document}

### 2022-04-22 paper.tex
Other material

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes}

\author{\IEEEauthorblockN{Samuel Kostadinov}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{University of Trento}\\
Trento, Italy \\
samuel.kostadinov@unitn.it}

\maketitle

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
Typicality, Prototypes, CNNs, Siamese Network
\end{IEEEkeywords}

\section{Introduction}

	The typicality of a concept is a topic that needs a lot of exploration, since it's difficult to evaluate precisely the typicality of an object 
	and also because the people's brains are always a little different from each other. The experiment I would like to propose, has the objective of 
	make sure we can understand better the bond between the perceived typicality of an object that belongs to a category and the prototype of that category.
	This can help the scientists to better understand how knowledge is organized in the brain. This experiment consists in different phases, such as
	data collection, feature extraction, prototype construction and similarity judgment.

\section{Related Work}

	In this section we will cover some related work to the topics that are of interest for this paper. In section \ref{featureExtractionSubSection} there is  an overview on 
	feature extraction methods, in section \ref{PrototypeContructionSubSection} there are prototype construction related work, and in section \ref{SimilarityJudgmentSubSection} there is an 
	outline of similarity judgment related work.

	\subsection{Feature extraction related work}\label{featureExtractionSubSection}
	\subsection{Prototype construction related work}\label{PrototypeContructionSubSection}
	\subsection{Similarity judgment related work}\label{SimilarityJudgmentSubSection}

\section{Background}
\section{Data Collection}
\section{Feature Extraction}
\section{Prototype Construction}
\section{Similarity Judgment}

\section{Conclusion}
\section{Possible Further Experiments}

%\section{Ease of Use}
%
%\subsection{Maintaining the Integrity of the Specifications}
%
%The IEEEtran class file is used to format your paper and style the text. All margins, 
%column widths, line spaces, and text fonts are prescribed; please do not 
%alter them. You may note peculiarities. For example, the head margin
%measures proportionately more than is customary. This measurement 
%and others are deliberate, using specifications that anticipate your paper 
%as one part of the entire proceedings, and not as an independent document. 
%Please do not revise any of the current designations.
%
%
%
%
%
%\section{Prepare Your Paper Before Styling}
%Before you begin to format your paper, first write and save the content as a 
%separate text file. Complete all content and organizational editing before 
%formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
%proofreading, spelling and grammar.
%
%Keep your text and graphic files separate until after the text has been 
%formatted and styled. Do not number text heads---{\LaTeX} will do that 
%for you.
%
%\subsection{Abbreviations and Acronyms}\label{AA}
%Define abbreviations and acronyms the first time they are used in the text, 
%even after they have been defined in the abstract. Abbreviations such as 
%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
%abbreviations in the title or heads unless they are unavoidable.
%
%\subsection{Units}
%\begin{itemize}
%\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
%\end{itemize}
%
%\subsection{Equations}
%Number equations consecutively. To make your 
%equations more compact, you may use the solidus (~/~), the exp function, or 
%appropriate exponents. Italicize Roman symbols for quantities and variables, 
%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
%sign. Punctuate equations with commas or periods when they are part of a 
%sentence, as in:
%\begin{equation}
%a+b=\gamma\label{eq}
%\end{equation}
%
%Be sure that the 
%symbols in your equation have been defined before or immediately following 
%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
%
%\subsection{\LaTeX-Specific Advice}
%
%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
%to combine sections, add equations, or change the order of figures or
%citations without having to go through the file line by line.
%
%Please don't use the \verb|{eqnarray}| equation environment. Use
%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
%environment leaves unsightly spaces around relation symbols.
%
%Please note that the \verb|{subequations}| environment in {\LaTeX}
%will increment the main equation counter even when there are no
%equation numbers displayed. If you forget that, you might write an
%article in which the equation numbers skip from (17) to (20), causing
%the copy editors to wonder if you've discovered a new method of
%counting.
%
%{\BibTeX} does not work by magic. It doesn't get the bibliographic
%data from thin air but from .bib files. If you use {\BibTeX} to produce a
%bibliography you must send the .bib files. 
%
%{\LaTeX} can't read your mind. If you assign the same label to a
%subsubsection and a table, you might find that Table I has been cross
%referenced as Table IV-B3. 
%
%{\LaTeX} does not have precognitive abilities. If you put a
%\verb|\label| command before the command that updates the counter it's
%supposed to be using, the label will pick up the last counter to be
%cross referenced instead. In particular, a \verb|\label| command
%should not go before the caption of a figure or a table.
%
%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
%will not stop equation numbers inside \verb|{array}| (there won't be
%any anyway) and it might stop a wanted equation number in the
%surrounding equation.
%
%\subsection{Some Common Mistakes}\label{SCM}
%\begin{itemize}
%\item The word ``data'' is plural, not singular.
%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
%\item Do not confuse ``imply'' and ``infer''.
%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
%\end{itemize}
%An excellent style manual for science writers is \cite{b7}.
%
%\subsection{Authors and Affiliations}
%\textbf{The class file is designed for, but not limited to, six authors.} A 
%minimum of one author is required for all conference articles. Author names 
%should be listed starting from left to right and then moving down to the 
%next line. This is the author sequence that will be used in future citations 
%and by indexing services. Names should not be listed in columns nor group by 
%affiliation. Please keep your affiliations as succinct as possible (for 
%example, do not differentiate among departments of the same organization).
%
%\subsection{Identify the Headings}
%Headings, or heads, are organizational devices that guide the reader through 
%your paper. There are two types: component heads and text heads.
%
%Component heads identify the different components of your paper and are not 
%topically subordinate to each other. Examples include Acknowledgments and 
%References and, for these, the correct style to use is ``Heading 5''. Use 
%``figure caption'' for your Figure captions, and ``table head'' for your 
%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
%style (in this case, italic) in addition to the style provided by the drop 
%down menu to differentiate the head from the text.
%
%Text heads organize the topics on a relational, hierarchical basis. For 
%example, the paper title is the primary text head because all subsequent 
%material relates and elaborates on this one topic. If there are two or more 
%sub-topics, the next level head (uppercase Roman numerals) should be used 
%and, conversely, if there are not at least two sub-topics, then no subheads 
%should be introduced.
%
%\subsection{Figures and Tables}
%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
%bottom of columns. Avoid placing them in the middle of columns. Large 
%figures and tables may span across both columns. Figure captions should be 
%below the figures; table heads should appear above the tables. Insert 
%figures and tables after they are cited in the text. Use the abbreviation 
%``Fig.~\ref{fig}'', even at the beginning of a sentence.
%
%\begin{table}[htbp]
%\caption{Table Type Styles}
%\begin{center}
%\begin{tabular}{|c|c|c|c|}
%\hline
%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
%\cline{2-4} 
%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
%\hline
%copy& More table copy$^{\mathrm{a}}$& &  \\
%\hline
%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
%\end{tabular}
%\label{tab1}
%\end{center}
%\end{table}
%
%\begin{figure}[htbp]
%\centerline{\includegraphics{fig1.png}}
%\caption{Example of a figure caption.}
%\label{fig}
%\end{figure}
%
%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
%rather than symbols or abbreviations when writing Figure axis labels to 
%avoid confusing the reader. As an example, write the quantity 
%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
%units in the label, present them within parentheses. Do not label axes only 
%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
%quantities and units. For example, write ``Temperature (K)'', not 
%``Temperature/K''.

%\section*{Acknowledgment}
%
%The preferred spelling of the word ``acknowledgment'' in America is without 
%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
%acknowledgments in the unnumbered footnote on the first page.

%\section*{References}
%
%Please number citations consecutively within brackets \cite{b1}. The 
%sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
%number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
%the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
%
%Number footnotes separately in superscripts. Place the actual footnote at 
%the bottom of the column in which it was cited. Do not put footnotes in the 
%abstract or reference list. Use letters for table footnotes.
%
%Unless there are six authors or more give all authors' names; do not use 
%``et al.''. Papers that have not been published, even if they have been 
%submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
%that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
%Capitalize only the first word in a paper title, except for proper nouns and 
%element symbols.
%
%For papers published in translation journals, please give the English 
%citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}

%\vspace{12pt}
%\color{red}
%IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2022-04-24 paper.tex
Started background section, changed readme, bibliography not working

@@
 \usepackage{xcolor}
+%\usepackage{bibtex}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-	In this section we will cover some related work to the topics that are of interest for this paper. In section \ref{featureExtractionSubSection} there is  an overview on 
-	feature extraction methods, in section \ref{PrototypeContructionSubSection} there are prototype construction related work, and in section \ref{SimilarityJudgmentSubSection} there is an 
+	In this section we will cover some related work to the topics that are of interest for this paper. In the first section there is an overview on 
+	feature extraction methods, in the second section there are prototype construction related work, and in the final section there is an 
 	outline of similarity judgment related work.
 
-	\subsection{Feature extraction related work}\label{featureExtractionSubSection}
-	\subsection{Prototype construction related work}\label{PrototypeContructionSubSection}
-	\subsection{Similarity judgment related work}\label{SimilarityJudgmentSubSection}
+	\subsection{Feature extraction related work}\label{fes}	
+	\subsection{Prototype construction related work}\label{pcs}
+	\subsection{Similarity judgment related work}\label{sjs}
 
 \section{Background}
+
+	\subsection{Feature extraction}
+
+		Feature extraction is a topic widely studied. 
+		This topic has numerous different applications. 
+		One of its goals is to reduce the amount of computational power needed for image processing. 
+		There are various techniques to extract meaningful features from images. 
+		Some of them are very common and very easy to implement. 
+		These are, for example, edge extraction or shape analysis. 
+		Other possibilities, more advanced, involve neural networks.\\
+
+		\begin{itemize}
+
+			\item \textbf{Edge detection}:\\				
+				In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
+				These are usually divided into two groups, gradient-based and gaussian-based. 
+				Some examples are the Sobel operator and the Canny edge detector. 
+				Each of the methods has pros and cons. 
+				It's the user's job to find the most appropriate for its goal~\cite{1}.
+
+		\end{itemize}
+
 \section{Data Collection}
@@
 \section{Possible Further Experiments}
-
-%\section{Ease of Use}
-%
-%\subsection{Maintaining the Integrity of the Specifications}
-%
-%The IEEEtran class file is used to format your paper and style the text. All margins, 
-%column widths, line spaces, and text fonts are prescribed; please do not 
-%alter them. You may note peculiarities. For example, the head margin
-%measures proportionately more than is customary. This measurement 
-%and others are deliberate, using specifications that anticipate your paper 
-%as one part of the entire proceedings, and not as an independent document. 
-%Please do not revise any of the current designations.
-%
-%
-%
-%
-%
-%\section{Prepare Your Paper Before Styling}
-%Before you begin to format your paper, first write and save the content as a 
-%separate text file. Complete all content and organizational editing before 
-%formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-%proofreading, spelling and grammar.
-%
-%Keep your text and graphic files separate until after the text has been 
-%formatted and styled. Do not number text heads---{\LaTeX} will do that 
-%for you.
-%
-%\subsection{Abbreviations and Acronyms}\label{AA}
-%Define abbreviations and acronyms the first time they are used in the text, 
-%even after they have been defined in the abstract. Abbreviations such as 
-%IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-%abbreviations in the title or heads unless they are unavoidable.
-%
-%\subsection{Units}
-%\begin{itemize}
-%\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-%\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-%\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-%\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-%\end{itemize}
-%
-%\subsection{Equations}
-%Number equations consecutively. To make your 
-%equations more compact, you may use the solidus (~/~), the exp function, or 
-%appropriate exponents. Italicize Roman symbols for quantities and variables, 
-%but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-%sign. Punctuate equations with commas or periods when they are part of a 
-%sentence, as in:
-%\begin{equation}
-%a+b=\gamma\label{eq}
-%\end{equation}
-%
-%Be sure that the 
-%symbols in your equation have been defined before or immediately following 
-%the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-%the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-%
-%\subsection{\LaTeX-Specific Advice}
-%
-%Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-%of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-%to combine sections, add equations, or change the order of figures or
-%citations without having to go through the file line by line.
-%
-%Please don't use the \verb|{eqnarray}| equation environment. Use
-%\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-%environment leaves unsightly spaces around relation symbols.
-%
-%Please note that the \verb|{subequations}| environment in {\LaTeX}
-%will increment the main equation counter even when there are no
-%equation numbers displayed. If you forget that, you might write an
-%article in which the equation numbers skip from (17) to (20), causing
-%the copy editors to wonder if you've discovered a new method of
-%counting.
-%
-%{\BibTeX} does not work by magic. It doesn't get the bibliographic
-%data from thin air but from .bib files. If you use {\BibTeX} to produce a
-%bibliography you must send the .bib files. 
-%
-%{\LaTeX} can't read your mind. If you assign the same label to a
-%subsubsection and a table, you might find that Table I has been cross
-%referenced as Table IV-B3. 
-%
-%{\LaTeX} does not have precognitive abilities. If you put a
-%\verb|\label| command before the command that updates the counter it's
-%supposed to be using, the label will pick up the last counter to be
-%cross referenced instead. In particular, a \verb|\label| command
-%should not go before the caption of a figure or a table.
-%
-%Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-%will not stop equation numbers inside \verb|{array}| (there won't be
-%any anyway) and it might stop a wanted equation number in the
-%surrounding equation.
-%
-%\subsection{Some Common Mistakes}\label{SCM}
-%\begin{itemize}
-%\item The word ``data'' is plural, not singular.
-%\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-%\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-%\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-%\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-%\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-%\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-%\item Do not confuse ``imply'' and ``infer''.
-%\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-%\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-%\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-%\end{itemize}
-%An excellent style manual for science writers is \cite{b7}.
-%
-%\subsection{Authors and Affiliations}
-%\textbf{The class file is designed for, but not limited to, six authors.} A 
-%minimum of one author is required for all conference articles. Author names 
-%should be listed starting from left to right and then moving down to the 
-%next line. This is the author sequence that will be used in future citations 
-%and by indexing services. Names should not be listed in columns nor group by 
-%affiliation. Please keep your affiliations as succinct as possible (for 
-%example, do not differentiate among departments of the same organization).
-%
-%\subsection{Identify the Headings}
-%Headings, or heads, are organizational devices that guide the reader through 
-%your paper. There are two types: component heads and text heads.
-%
-%Component heads identify the different components of your paper and are not 
-%topically subordinate to each other. Examples include Acknowledgments and 
-%References and, for these, the correct style to use is ``Heading 5''. Use 
-%``figure caption'' for your Figure captions, and ``table head'' for your 
-%table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-%style (in this case, italic) in addition to the style provided by the drop 
-%down menu to differentiate the head from the text.
-%
-%Text heads organize the topics on a relational, hierarchical basis. For 
-%example, the paper title is the primary text head because all subsequent 
-%material relates and elaborates on this one topic. If there are two or more 
-%sub-topics, the next level head (uppercase Roman numerals) should be used 
-%and, conversely, if there are not at least two sub-topics, then no subheads 
-%should be introduced.
-%
 %\subsection{Figures and Tables}
@@
 
-%\section*{Acknowledgment}
-%
-%The preferred spelling of the word ``acknowledgment'' in America is without 
-%an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-%G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-%acknowledgments in the unnumbered footnote on the first page.
-
 %\section*{References}
@@
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
+
+\bibitem{1} J.
+S.
+Owotogbe,T.
+S.
+Ibiyemi, and B.
+A.
+Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol.
+4, issue 11, Nov.
+2019
+
+%\bibitem{b1} J.
+S.
+Owotogbe,T.
+S.
+Ibiyemi, and B.
+A.
+Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol.
+4, pp.
+11, November 2019.
+%\bibitem{1} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+%\bibitem{b6} Y.
 Yorozu, M.
@@
 301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
 \end{thebibliography}

### 2022-04-24 paper.tex
removed related work section

@@
 
-\section{Related Work}
+%\section{Related Work}
 
-	In this section we will cover some related work to the topics that are of interest for this paper. In the first section there is an overview on 
-	feature extraction methods, in the second section there are prototype construction related work, and in the final section there is an 
-	outline of similarity judgment related work.
+%	In this section we will cover some related work to the topics that are of interest for this paper. In the first section there is an overview on 
+%	feature extraction methods, in the second section there are prototype construction related work, and in the final section there is an 
+%	outline of similarity judgment related work.
 
-	\subsection{Feature extraction related work}\label{fes}	
-	\subsection{Prototype construction related work}\label{pcs}
-	\subsection{Similarity judgment related work}\label{sjs}
+%	\subsection{Feature extraction related work}\label{fes}	
+%	\subsection{Prototype construction related work}\label{pcs}
+%	\subsection{Similarity judgment related work}\label{sjs}
 

### 2022-05-06 paper.tex
Updated material and work in progress on main

--- 2022-04-24 paper.tex
@@
 \usepackage{xcolor}
-%\usepackage{bibtex}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\section{Related Work}
-
-	In this section we will cover some related work to the topics that are of interest for this paper. In the first section there is an overview on 
-	feature extraction methods, in the second section there are prototype construction related work, and in the final section there is an 
-	outline of similarity judgment related work.
-
-	\subsection{Feature extraction related work}\label{fes}	
-	\subsection{Prototype construction related work}\label{pcs}
-	\subsection{Similarity judgment related work}\label{sjs}
-
 \section{Background}
@@
 
+			\subsubsection{Classic feature extraction techniques}\\
+
+				One of the first feature extraction methods implemented in image processing is edge detection.				
+				In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
+				These are usually divided into two groups, gradient-based and Gaussian-based. 
+				Some examples are the Sobel operator and the Canny edge detector. 
+				Each of the methods has pros and cons. 
+				It's the user's job to find the most appropriate for its goal~\cite{1}.\\
+
+				After edge detection, other techniques began to spread for feature extraction. 
+				In a paper by Kumar and Kumar Bhatia written in 2014 \cite{2}, 
+				there are some examples of techniques used to extract features. 
+				In the first one, the authors present different types of features and then some techniques to extract them. 
+				These are:
+
 				\begin{itemize}
 
-			\item \textbf{Edge detection}:\\				
-				In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
-				These are usually divided into two groups, gradient-based and gaussian-based. 
-				Some examples are the Sobel operator and the Canny edge detector. 
-				Each of the methods has pros and cons. 
-				It's the user's job to find the most appropriate for its goal~\cite{1}.
+					\item \textbf{Diagonal based feature extraction techniques}:
+
+						In this procedure, the image is divided into zones formed by small squares of pixels. 
+						In this case, there would be 19 diagonal lines. 
+						The value of each pixel in these diagonals is summed to obtain a single sub feature. 
+						Then we can extract a feature by averaging the sub features. 
+						With this method, we can extract a feature for every zone. 
+						Then by averaging the column-wise and row-wise features we can increase their number.
+
+					\item \textbf{Fourier descriptors}:
+
+						The Fourier transform is commonly used for shape analysis. 
+						The Fourier transformed coefficient form the Fourier descriptors. 
+						These descriptors represent the shape in a frequency domain, with the low frequencies symbolizing the general shape and the high frequencies symbolizing details of the shape. 
+						Since the transformation usually generates many parameters, only a subset is considered.
+
+					\item \textbf{Principal Component Analysis(PCA)}:
+
+						This procedure is a mathematical way to convert a set of observations into a set of values of uncorrelated variables. 
+						These variables are defined so that the first one has the highest variance, and the components are all orthogonal (independent) from each other.
+
+					\item \textbf{Independent component analysis(ICA)}:
+
+						ICA is a statistical technique. 
+						It aims to use non-Gaussian random variables to represent multidimensional vectors. 
+						The random variables should be as independent as possible.
+
+					\item \textbf{Gabor filter}:
+
+						A Gabor is a sinusoid multiplied by a Gaussian, and its response is a convolution operation. 
+						This type of filter performs well in both spatial and frequency domains.
+
+					\item \textbf{Chain Code Histogram of Character Contour}:
+
+						This method is based on a contour following technique. 
+						The contour following uses a chain coding standard proposed by Freeman, that assigns a value to every pixel to identify the next pixel in the border.
+
+					\item \textbf{Finding Intersection/Junction in character}:
+
+						Using the same standard proposed by Freeman used in Chain Code Histogram, there is the possibility to count intersections (or junctions) and open ends in a figure.
+
+					\item \textbf{Transition feature}:
+
+						This method is based on the transition from background to foreground. 
+						There are different techniques that can work both on grey level images or in 4-connected or 8-connected images.
 
 				\end{itemize}
+
+			\noindent These were not the only techniques presented in the paper, but since some were more problem-specific (about handwritten character recognition)
+			were excluded from the list. These excluded techniques can still be used, but may have worse results or may require some adaptation. 
+			The techniques were: Fractal theory techniques, Shadow features of character, Sector approach for feature extraction, 
+			Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.
+			In another paper, written in 2013 by Tian \cite{3}, there are some other techniques cited that may result useful:
+
+			\begin{itemize}
+
+				\item \textbf{Color features}:
+
+					Color is one of the most important features humans can perceive. 
+					The features we can extract depend on the color space, but once it's defined there are some possibilities. 
+					A few examples are color histograms, color moments and color coherence vectors. 
+					One of the simple and meaningful, according to the authors, is color moments. 
+					The most common color moments are the mean, the standard deviation and the skewness.
+
+				\item \textbf{Texture features}:
+
+					Another very important feature of images is texture. 
+					Features involving texture analysis can be extracted from groups of pixels. 
+					One of the most common methods is a Gabor filter, which can be used by characterizing the central frequency and the orientation parameters.
+
+			\end{itemize}
+
+		\subsubsection{Deformable shape analysis}
+
+			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular,
+
+		\subsubsection{Machine learning based feature extraction techniques}
+
+		%\subsubsection{Madical imaging feature extraction techniques}
+
+		\subsubsection{Hyperspectral images feature extraction}
 
@@
 %``Temperature/K''.
-
-%\section*{References}
-%
-%Please number citations consecutively within brackets \cite{b1}. The 
-%sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-%number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-%the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-%
-%Number footnotes separately in superscripts. Place the actual footnote at 
-%the bottom of the column in which it was cited. Do not put footnotes in the 
-%abstract or reference list. Use letters for table footnotes.
-%
-%Unless there are six authors or more give all authors' names; do not use 
-%``et al.''. Papers that have not been published, even if they have been 
-%submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-%that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-%Capitalize only the first word in a paper title, except for proper nouns and 
-%element symbols.
-%
-%For papers published in translation journals, please give the English 
-%citation first, followed by the original foreign-language citation \cite{b6}.
+-
 
@@
 2019
+\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, ``A Detailed Review of Feature Extraction in Image Processing Systems'', FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
+\bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
+\bibitem{4} Pedro F.
+Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol.
+27, no.
+2, pp.
+208-220, Feb.
+2005, doi: \url{https://doi.org/10.1109/TPAMI.2005.35}
 
@@
 4, pp.
-11, November 2019.
+11, Nov.
+2019
 %\bibitem{1} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
@@
 
-%\vspace{12pt}
-%\color{red}
-%IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}

### 2022-05-11 paper.tex
Done classical FE techniques

@@
 
-			\subsubsection{Classic feature extraction techniques}\\
+			\subsubsection{Classic feature extraction techniques}
 
@@
 
-					\item \textbf{Principal Component Analysis(PCA)}:
+					\item \textbf{Principal Component Analysis (PCA)}:
 
@@
 
-					\item \textbf{Independent component analysis(ICA)}:
+					\item \textbf{Independent component analysis (ICA)}:
 
@@
 			The techniques were: Fractal theory techniques, Shadow features of character, Sector approach for feature extraction, 
-			Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.
+			Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.\\
 			In another paper, written in 2013 by Tian \cite{3}, there are some other techniques cited that may result useful:
@@
 
-			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular,
+			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
+			In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{5}. For the goal of the experiment proposed here, some deformable shape 
+			detection techniques can be useful. \\
+			The technique proposed strongly relies on the trinagulated polygon representation.
+This type of representation lets approximate every 2D shape without holes using a representation based on triangles.
+			%The resulting approximation is as precise as the user decides, meaning that it's very flexible for the representation of shapes. 
+			%In particular, in the paper the triangulation was done with a technique called constrained Delaunay triangulation (CDT), because of its tight relation with the medial axis transform. 
+			The author also make use of the properties of chordal graphs and k-trees.\\
+			The technique described in this paper falls under the category of deformable template matching.
+One of the components of the method is the energy function, a function that associates a cost with every
+			possible transformation.
+The objective is to find the transformation with the lowest possible cost.
+This component is very flexible, since depending on the formulation of the energy function the costs
+			can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
+			Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually requires an initialization near to the correct solution, 
+			although this is not required for the algorithm presented in this paper. 
+			For the implementation of the algorithm itself, a techniques called nonserial dynamic programming was the key factor.
+In fact, using the order of perfect elimination (property of the every triangulated
+			simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
+			update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
+			The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
+			energy cost, which corresponds to the best template match.
 
@@
 \section{Possible Further Experiments}
-%\subsection{Figures and Tables}
+
 %\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
@@
 %``Fig.~\ref{fig}'', even at the beginning of a sentence.
-%
+
 %\begin{table}[htbp]
@@
 %\end{table}
-%
+
 %\begin{figure}[htbp]
@@
 %\end{figure}
-%
-%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-%rather than symbols or abbreviations when writing Figure axis labels to 
-%avoid confusing the reader. As an example, write the quantity 
-%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-%units in the label, present them within parentheses. Do not label axes only 
-%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-%quantities and units. For example, write ``Temperature (K)'', not 
-%``Temperature/K''.
--
+
+%\appendix
+
+%\section{Chordal graphs and k-trees}
 
@@
 \bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
-\bibitem{4} Pedro F.
+\bibitem{4} Chiranji Lal Chowdhary, D.P.Acharjya, Segmentation and Feature Extraction in Medical Imaging: A Systematic Review, vol.
+167, pp.
+26-36, Sep.
+2019, doi: \url{https://doi.org/10.1016/j.procs.2020.03.179}
+\bibitem{5} Pedro F.
 Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol.
@@
 
-%\bibitem{b1} J.
-S.
-Owotogbe,T.
-S.
-Ibiyemi, and B.
-A.
-Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol.
-4, pp.
-11, Nov.
-2019
-%\bibitem{1} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-%\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
 \end{thebibliography}
-
 \end{document}

### 2022-05-13 paper.tex
Almost done ML part of Feature Extraction

@@
 			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
-			In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{5}. For the goal of the experiment proposed here, some deformable shape 
+			In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{4}. For the goal of the experiment proposed here, some deformable shape 
 			detection techniques can be useful. \\
@@
 
-		%\subsubsection{Madical imaging feature extraction techniques}
+			After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
+			In 2019, Halimi et al. wrote a paper about a feature extraction technique that they implemented using unsupervised deep learning~\cite{5}. Although this paper examines the techniques for 
+			3D shapes, it's very likely that it can be adapted to extract 2D features from images.\\
+			The background of this experiments is formed of some concepts that are not immediate. One of the concepts used as background is the minimum distortion correspondence. The other are, for example, 
+			descriptor learning, functional maps and deep functional maps. These concepts serve as a base for all the work done later. \\
+			In particular, the authors focus on unsupervised deep functional maps. The authors state that the main contribution of their paper is that they introduce a technique with which they can 
+			avoid annotating a lot of data before training a model. After reducing the number of vertices to a number between 5000 and 7000, the authors used a deep functional map network. The inputs are 
+			fed to two redisual neural networks, which compute a dense descriptor fields.
+These descriptors, are the inputs to the functional map layer.
+Lastly, as post processing, a point-wise map recovery was
+			applied and, after that, the shape was upscaled to the original resolution.
+
+			\noindent In 2019, there is another paper, written by Varshni et al. that proposes another method~\cite{6}. This paper has the objective to classify images suing CNNs to understand if a patient 
+			has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
+			In this paper's results it's reported that the best model architecture is DenseNet-169.
+This kind of neural netowrk, called Dense Nets, overcomes the problem of gradient vanishing.
+The model used in
+			particular for the work of this paper had 4 dense blocks and 3 transition layers. Then there is a classification layer.
+
+			\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumors. The process described in the paper is divided into three points. The 
+			first one is preprocessing, the second is feature extraction and the third is brain tumor classification. The first step is just to rescale the values to the range $[0,\ 1]$. The feature extractor 
+			used is the GIST descriptor. The GIST is then combined with a Gabor filter and produces a total of $mxnx4x4$ GIST feature vectors. There is a variant of the GIST descriptor, the 
+			PCA-NGIST is a PCA-based normalized GIST feature extraction method.
+The NGIST is a normalized version of the GIST descriptor, that uses the L2 norm to make the GIST invariant to illumination and shadowing.
+			After this step, the only thing left is the classification of the tumor, which was performed with a RELM classifier.
 
 		\subsubsection{Hyperspectral images feature extraction}
+
+		\subsubsection{Considerations about feature extraction}
+
+		\subsection{Networks}
+
+		\subsubsection{Convolutional Neural Network}
+
+		\subsubsection{Siamese Neural Network}
 
@@
 A.
-Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol.
+Adu, Edge Detection Techniques on Digital Images - A Review, International Journal of Innovative Science and Research Technology, vol.
 4, issue 11, Nov.
 2019
-\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, ``A Detailed Review of Feature Extraction in Image Processing Systems'', FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
+\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, A Detailed Review of Feature Extraction in Image Processing Systems, FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
 \bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
-\bibitem{4} Chiranji Lal Chowdhary, D.P.Acharjya, Segmentation and Feature Extraction in Medical Imaging: A Systematic Review, vol.
-167, pp.
-26-36, Sep.
-2019, doi: \url{https://doi.org/10.1016/j.procs.2020.03.179}
-\bibitem{5} Pedro F.
+\bibitem{4} Pedro F.
 Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol.
@@
 2005, doi: \url{https://doi.org/10.1109/TPAMI.2005.35}
+\bibitem{5} Halimi, Oshri and Litany, Or and Rodola, Emanuele and Bronstein, Alex M and Kimmel, Ron, Unsupervised learning of dense shape correspondence, Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition, pp.
+4370-4379, 2019
+\bibitem{6} Varshni, Dimpy and Thakral, Kartik and Agarwal, Lucky and Nijhawan, Rahul and Mittal, Ankush, Pneumonia detection using CNN based feature extraction, 2019 IEEE international conference on electrical, computer and communication technologies (ICECCT), pp.
+1-7, 2019
+\bibitem{7} Gumaei, Abdu and Hassan, Mohammad Mehedi and Hassan, Md Rafiul and Alelaiwi, Abdulhameed and Fortino, Giancarlo, A hybrid feature extraction method with regularized extreme learning machine for brain tumor classification, vol.
+7, pp.
+36266--36273, 2019
 

### 2022-05-16 paper.tex
Done machine learning feature extraction
Added material and began CNN baground

@@
 \begin{abstract}
+
+	Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
 
@@
 						This method is based on the transition from background to foreground. 
-						There are different techniques that can work both on grey level images or in 4-connected or 8-connected images.
+						There are different techniques that can work both on gray level images or in 4-connected or 8-connected images.
 
@@
 				detection techniques can be useful. \\
-			The technique proposed strongly relies on the trinagulated polygon representation.
+				The technique proposed strongly relies on the triangulated polygon representation.
 This type of representation lets approximate every 2D shape without holes using a representation based on triangles.
@@
 				although this is not required for the algorithm presented in this paper. 
-			For the implementation of the algorithm itself, a techniques called nonserial dynamic programming was the key factor.
+				For the implementation of the algorithm itself, a techniques called non-serial dynamic programming was the key factor.
 In fact, using the order of perfect elimination (property of the every triangulated
@@
 
-		\subsubsection{Machine learning based feature extraction techniques}
+			\subsubsection{Machine learning based feature extraction techniques} \label{mlfe}
 
@@
 				avoid annotating a lot of data before training a model. After reducing the number of vertices to a number between 5000 and 7000, the authors used a deep functional map network. The inputs are 
-			fed to two redisual neural networks, which compute a dense descriptor fields.
+				fed to two residual neural networks, which compute a dense descriptor fields.
 These descriptors, are the inputs to the functional map layer.
@@
 				In this paper's results it's reported that the best model architecture is DenseNet-169.
-This kind of neural netowrk, called Dense Nets, overcomes the problem of gradient vanishing.
+This kind of neural network, called Dense Nets, overcomes the problem of gradient vanishing.
 The model used in
@@
 				\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumors. The process described in the paper is divided into three points. The 
-			first one is preprocessing, the second is feature extraction and the third is brain tumor classification. The first step is just to rescale the values to the range $[0,\ 1]$. The feature extractor 
+				first one is preprocessing, the second is feature extraction and the third is brain tumor classification.
+The first step is just to rescale the values to the range $[0,\ 1]$.
+The feature extractor
 				used is the GIST descriptor. The GIST is then combined with a Gabor filter and produces a total of $mxnx4x4$ GIST feature vectors. There is a variant of the GIST descriptor, the 
@@
 
+				Although there exists techniques that can extract features from hyperspectral images, this kind of images are created to capture the entire spectrum. This fact means that these images can capture 
+				more information then what the human eye can. techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent 
+				networks, as seen in a paper by Hu et al.~\cite{8} and in a paper by Rasti et al.~\cite{9}. Probably, it's more meaningful to use normal images than these ones, since, as just
+
 			\subsubsection{Considerations about feature extraction}
+
+				Although there are different methods to extract feature, the ones that require neural networks are not easily understandable by humans. The classic feature extraction techniques have a more 
+				human comprehensible result, while the machine learning techniques extract feature in the form of vectors of attributes.
+Both of these can be used in the following steps, but the procedure requires
+				little adjustments in the steps based on the chosen procedure.
 
@@
 
-		\subsubsection{Convolutional Neural Network}
+			Neural Networks are a powerful instrument in the hands of computer scientists.
+There exists a lot of different types of artificial neural networks, each with its own peculiarities.
+In particular, for this
+			experiment the one needed will be, most likely, just convolutional neural networks and siamese neural networks.
+
+			\subsubsection{Convolutional Neural Network (CNN)}
+
+				Convolutional neural networks are not an extremely recent type of neural network, especially if we consider that LeNet-5 was created in 1998.
+Scientists have dealt with CNNs for some years.
+Now, as of 2022,
+				CNNs are mostly used to deal with images.\\
+				In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs~\cite{10}. These networks use mostly three kind of layers: Dense layers (which are fully connected layers), 
+				convolution layers and pooling layers. In the following, there will be a short description of each kind of layer. 
+				\begin{itemize}
+
+					\item \textbf{Dense layer}:\\
+						The dense layer is not peculiar of CNNs, in fact it's found in almost all types of neural networks. It consists of a set of neurons that are connected with every neuron of the previous 
+						layer. Dense layers are usually used towards the end of the network.
+
+					\item \textbf{Convolutional layer}:\\
+						Convolutional layers just compute a convolution operation. This helps reducing the input size and extract meaningful features from the image taken as input. These layers are usually used 
+						in the first layers of the neural network.
+
+					\item \textbf{Pooling layers}:\\
+						Pooling layers downsamples the image to reducing the number of parameters needed.
+These layers are usually alternated with the convolution layers, so are used at the beginning of a neural network.
+
+				\end{itemize}
+
+				The applications of deep learning and CNNs are numerous. As shown in \ref{mlfe} there are some CNNs used in image classification with the objective to identify diseases. The typical example is 
+				the pneumonia detection. Another possibility is to use CNNs in segmentation or self driving cars, as stated in \cite{11} by Alzubaidi et al.
 
@@
 
-%\appendix
-
-%\section{Chordal graphs and k-trees}
-
 \begin{thebibliography}{00}
@@
 2019
-\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, A Detailed Review of Feature Extraction in Image Processing Systems, FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
+\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, A Detailed Review of Feature Extraction in Image Processing Systems, Fourth International Conference on Advanced Computing \& Communication Technologies, DOI: https://doi.org/10.1109/ACCT.2014.7, 2014
 \bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
@@
 208-220, Feb.
-2005, doi: \url{https://doi.org/10.1109/TPAMI.2005.35}
+2005, doi: https://doi.org/10.1109/TPAMI.2005.35
 \bibitem{5} Halimi, Oshri and Litany, Or and Rodola, Emanuele and Bronstein, Alex M and Kimmel, Ron, Unsupervised learning of dense shape correspondence, Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition, pp.
@@
 36266--36273, 2019
+\bibitem{8} Hu, Wen-Shuai and Li, Heng-Chao and Pan, Lei and Li, Wei and Tao, Ran and Du, Qian, Spatial--spectral feature extraction via deep ConvLSTM neural networks for hyperspectral image classification, vol.
+58, pp.
+4237--4250, 2020
+\bibitem{9} Rasti, Behnood and Hong, Danfeng and Hang, Renlong and Ghamisi, Pedram and Kang, Xudong and Chanussot, Jocelyn and Benediktsson, Jon Atli, Feature extraction for hyperspectral imagery: The evolution from shallow to deep: Overview and toolbox, IEEE Geoscience and Remote Sensing Magazine, vol.8, pp.60-88, 2020
+\bibitem{10} Jianxin Wu, Introduction to convolutional neural networks, National Key Lab for Novel Software Technology. Nanjing University. China, vol. 5, n. 33, 2017
+\bibitem{11} Alzubaidi, Laith and Zhang, Jinglan and Humaidi, Amjad J and Al-Dujaili, Ayad and Duan, Ye and Al-Shamma, Omran and Santamaría, J and Fadhel, Mohammed A and Al-Amidie, Muthana and Farhan, Laith, Review of deep learning: Concepts, CNN architectures, challenges, applications, future directions, Journal of big Data, vol.
+8, pp.
+1-74, 2021
 

### 2022-05-16 paper.tex
Done background on NNs

@@
 						In this procedure, the image is divided into zones formed by small squares of pixels. 
-						In this case, there would be 19 diagonal lines. 
+						In the paper's case, there would be 19 diagonal lines. 
 						The value of each pixel in these diagonals is summed to obtain a single sub feature. 
@@
 					\item \textbf{Pooling layers}:\\
-						Pooling layers downsamples the image to reducing the number of parameters needed.
+						Pooling layers downsample the image to reducing the number of parameters needed.
 These layers are usually alternated with the convolution layers, so are used at the beginning of a neural network.
@@
 
-				The applications of deep learning and CNNs are numerous. As shown in \ref{mlfe} there are some CNNs used in image classification with the objective to identify diseases. The typical example is 
+				The applications of deep learning and CNNs are numerous. As shown previously, there are some CNNs used in image classification with the objective to identify diseases. The typical example is 
 				the pneumonia detection. Another possibility is to use CNNs in segmentation or self driving cars, as stated in \cite{11} by Alzubaidi et al.
@@
 			\subsubsection{Siamese Neural Network}
+
+				Siamese neural networks, also called twin networks, are a more recent advance in computer science. These neural networks have a different structure from convolutional neural networks. The 
+				structure of siamese neural networks is peculiar.
+In fact, there are two identical networks that process different inputs and, after that, merge in a single layer that measures the similarity between
+				the two outputs of the two networks. The siamese neural networks have a different application compared to CNNs, in fact twin networks are mainly used to measure similarity of two objects. 
+				In the case of this paper, the siamese neural networks are used for image matching.
+This is not the first time that siamese networks are used for image matching, as proved by a paper written in 2016 by
+				Melekhov et al., but with a little difference in the objective of the matching. The objective of the paper was to learn a general similarity for image retrieval, while on the case of this 
+				paper, the objective is to find a similarity measure with a prototype.
 
@@
 1-74, 2021
+\bibitem{12} Melekhov, Iaroslav and Kannala, Juho and Rahtu, Esa, Siamese network features for image matching, 2016 23rd International Conference on Pattern Recognition (ICPR), vol.
+1, pp.
+378-388, 2016, doi:10.1109/ICPR.2016.7899663
 

### 2022-05-20 paper.tex
a little bit of cleaning of the material
Finished background, word count: 2717

@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
+% \IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{textcomp}
-\usepackage{xcolor}
+\usepackage{xcolour}
+\usepackage[backend=biber, sorting=none]{biblatex}
+\addbibresource{bibliography.bib}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 				Each of the methods has pros and cons. 
-				It's the user's job to find the most appropriate for its goal~\cite{1}.\\
+				It's the user's job to find the most appropriate for its goal~\cite{owotogbe2019edge}.\\
 
 				After edge detection, other techniques began to spread for feature extraction. 
-				In a paper by Kumar and Kumar Bhatia written in 2014 \cite{2}, 
+				In a paper by Kumar and Kumar Bhatia written in 2014 \cite{kumar2014detailed}, 
 				there are some examples of techniques used to extract features. 
@@
 			Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.\\
-			In another paper, written in 2013 by Tian \cite{3}, there are some other techniques cited that may result useful:
+			In another paper, written in 2013 by Tian \cite{ping2013review}, there are some other techniques cited that may result useful:
 
@@
 
-				\item \textbf{Color features}:
+				\item \textbf{colour features}:
 
-					Color is one of the most important features humans can perceive. 
-					The features we can extract depend on the color space, but once it's defined there are some possibilities. 
-					A few examples are color histograms, color moments and color coherence vectors. 
-					One of the simple and meaningful, according to the authors, is color moments. 
-					The most common color moments are the mean, the standard deviation and the skewness.
+					colour is one of the most important features humans can perceive. 
+					The features we can extract depend on the colour space, but once it's defined there are some possibilities. 
+					A few examples are colour histograms, colour moments and colour coherence vectors. 
+					One of the simple and meaningful, according to the authors, is colour moments. 
+					The most common colour moments are the mean, the standard deviation and the skewness.
 
@@
 				A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
-				In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{4}. For the goal of the experiment proposed here, some deformable shape 
+				In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{felzenszwalb2005representation}.
+For the goal of the experiment proposed here, some deformable shape
 				detection techniques can be useful. \\
@@
 				After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
-				In 2019, Halimi et al. wrote a paper about a feature extraction technique that they implemented using unsupervised deep learning~\cite{5}. Although this paper examines the techniques for 
+				In 2019, Halimi et al.
+wrote a paper about a feature extraction technique that they implemented using unsupervised deep learning~\cite{halimi2019unsupervised}.
+Although this paper examines the techniques for
 				3D shapes, it's very likely that it can be adapted to extract 2D features from images.\\
@@
 
-				\noindent In 2019, there is another paper, written by Varshni et al. that proposes another method~\cite{6}. This paper has the objective to classify images suing CNNs to understand if a patient 
+				\noindent In 2019, there is another paper, written by Varshni et al.
+that proposes another method~\cite{varshni2019pneumonia}.
+This paper has the objective to classify images suing CNNs to understand if a patient
 				has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
@@
 
-				\noindent In 2019, Guamei et al. wrote a paper about hybrid feature extraction methods to classify brain tumors. The process described in the paper is divided into three points. The 
-				first one is preprocessing, the second is feature extraction and the third is brain tumor classification.
+				\noindent In 2019, Guamei et al.
+wrote a paper about hybrid feature extraction methods to classify brain tumours~\cite{gumaei2019hybrid}.
+The process described in the paper is divided into three points.
+The
+				first one is preprocessing, the second is feature extraction and the third is brain tumour classification.
 The first step is just to rescale the values to the range $[0,\ 1]$.
@@
 The NGIST is a normalized version of the GIST descriptor, that uses the L2 norm to make the GIST invariant to illumination and shadowing.
-				After this step, the only thing left is the classification of the tumor, which was performed with a RELM classifier.
+				After this step, the only thing left is the classification of the tumour, which was performed with a RELM classifier.
 
@@
 				more information then what the human eye can. techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent 
-				networks, as seen in a paper by Hu et al.~\cite{8} and in a paper by Rasti et al.~\cite{9}. Probably, it's more meaningful to use normal images than these ones, since, as just
+				networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}.
+Probably, it's more meaningful to use normal images than these ones, since, as just
 
@@
 				CNNs are mostly used to deal with images.\\
-				In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs~\cite{10}. These networks use mostly three kind of layers: Dense layers (which are fully connected layers), 
+				In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs~\cite{wu2017introduction}.
+These networks use mostly three kind of layers: Dense layers (which are fully connected layers),
 				convolution layers and pooling layers. In the following, there will be a short description of each kind of layer. 
@@
 				The applications of deep learning and CNNs are numerous. As shown previously, there are some CNNs used in image classification with the objective to identify diseases. The typical example is 
-				the pneumonia detection. Another possibility is to use CNNs in segmentation or self driving cars, as stated in \cite{11} by Alzubaidi et al.
+				the pneumonia detection. Another possibility is to use CNNs in segmentation or self driving cars, as stated in \cite{alzubaidi2021review} by Alzubaidi et al.
 
@@
 This is not the first time that siamese networks are used for image matching, as proved by a paper written in 2016 by
-				Melekhov et al., but with a little difference in the objective of the matching. The objective of the paper was to learn a general similarity for image retrieval, while on the case of this 
+				Melekhov et al.~\cite{melekhov2016siamese}, but with a little difference in the objective of the matching.
+The objective of the paper was to learn a general similarity for image retrieval, while on the case of this
 				paper, the objective is to find a similarity measure with a prototype.
+
+		\subsection{Similarity judgments}
+
+			In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017~\cite{appalaraju2017image}.
+In this work they explore the possibility to
+			find a similarity measure for image retrieval. To achieve this goal, they implemented a siamese neural network that uses two identical multi-scale CNNs that share weights. The ouput of the 
+			network is binary, being $1$ the label to predict in case of negative examples and $0$ the label to predict in case of positive example.
+The loss function used in this work is a contrastive loss.
+This paper
+			then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspyred by curriculum learning, that helps reducing the training time. \\
+			This is not the only work that uses neural networks to learn similarity, in fact there are also other application fields for similarity study.
+One of them is healthcare, as shown in a paper by Suo et al., written in
+			2017, that introduces a model used to make personalized prediction of diseases for patients, basing the prediction on a similarity related method, learned using CNNs~\cite{8217759}.
+In this paper, before
+			learning the actual similarity measure, the authors processed the input through a CNN and performed a step they call ``Time fusion''. This step let them incorporate the time information and 
+			weight differently eventual symptoms based on their temporal distance from the onset of the disease. Only after this step the authors proceeded to learn a similarity metric, basing the learning 
+			on CNNs.\\
+			Another paper, written by Chopra et al.
+in 2005, used a method similar to the one written by Appalaraju.
+In this work, the authors used a siamese architecture to learn a similarity metric and applied it
+			in the field of face verification~\cite{chopra2005learning}.\\
+			More interestingly, there are also other papers, in particular a paper by Attarian et al. written in 2020 uses $VGG16$. This paper's goal is to use this CNN to predict human similarity 
+			judgments~\cite{attarian2020transforming}. Using $VGG16$, the authors were able to achieve good results, with over 90\% in validation accuracy.
 
@@
 
-%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-%bottom of columns. Avoid placing them in the middle of columns. Large 
-%figures and tables may span across both columns. Figure captions should be 
-%below the figures; table heads should appear above the tables. Insert 
-%figures and tables after they are cited in the text. Use the abbreviation 
-%``Fig.~\ref{fig}'', even at the beginning of a sentence.
+\nocite{*}
+\printbibliography
 
-%\begin{table}[htbp]
-%\caption{Table Type Styles}
-%\begin{center}
-%\begin{tabular}{|c|c|c|c|}
-%\hline
-%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-%\cline{2-4} 
-%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-%\hline
-%copy& More table copy$^{\mathrm{a}}$& &  \\
-%\hline
-%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-%\end{tabular}
-%\label{tab1}
-%\end{center}
-%\end{table}
-
-%\begin{figure}[htbp]
-%\centerline{\includegraphics{fig1.png}}
-%\caption{Example of a figure caption.}
-%\label{fig}
-%\end{figure}
-
-\begin{thebibliography}{00}
-
-\bibitem{1} J.
-S.
-Owotogbe,T.
-S.
-Ibiyemi, and B.
-A.
-Adu, Edge Detection Techniques on Digital Images - A Review, International Journal of Innovative Science and Research Technology, vol.
-4, issue 11, Nov.
-2019
-\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, A Detailed Review of Feature Extraction in Image Processing Systems, Fourth International Conference on Advanced Computing \& Communication Technologies, DOI: https://doi.org/10.1109/ACCT.2014.7, 2014
-\bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
-\bibitem{4} Pedro F.
-Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol.
-27, no.
-2, pp.
-208-220, Feb.
-2005, doi: https://doi.org/10.1109/TPAMI.2005.35
-\bibitem{5} Halimi, Oshri and Litany, Or and Rodola, Emanuele and Bronstein, Alex M and Kimmel, Ron, Unsupervised learning of dense shape correspondence, Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition, pp.
-4370-4379, 2019
-\bibitem{6} Varshni, Dimpy and Thakral, Kartik and Agarwal, Lucky and Nijhawan, Rahul and Mittal, Ankush, Pneumonia detection using CNN based feature extraction, 2019 IEEE international conference on electrical, computer and communication technologies (ICECCT), pp.
-1-7, 2019
-\bibitem{7} Gumaei, Abdu and Hassan, Mohammad Mehedi and Hassan, Md Rafiul and Alelaiwi, Abdulhameed and Fortino, Giancarlo, A hybrid feature extraction method with regularized extreme learning machine for brain tumor classification, vol.
-7, pp.
-36266--36273, 2019
-\bibitem{8} Hu, Wen-Shuai and Li, Heng-Chao and Pan, Lei and Li, Wei and Tao, Ran and Du, Qian, Spatial--spectral feature extraction via deep ConvLSTM neural networks for hyperspectral image classification, vol.
-58, pp.
-4237--4250, 2020
-\bibitem{9} Rasti, Behnood and Hong, Danfeng and Hang, Renlong and Ghamisi, Pedram and Kang, Xudong and Chanussot, Jocelyn and Benediktsson, Jon Atli, Feature extraction for hyperspectral imagery: The evolution from shallow to deep: Overview and toolbox, IEEE Geoscience and Remote Sensing Magazine, vol.8, pp.60-88, 2020
-\bibitem{10} Jianxin Wu, Introduction to convolutional neural networks, National Key Lab for Novel Software Technology. Nanjing University. China, vol. 5, n. 33, 2017
-\bibitem{11} Alzubaidi, Laith and Zhang, Jinglan and Humaidi, Amjad J and Al-Dujaili, Ayad and Duan, Ye and Al-Shamma, Omran and Santamaría, J and Fadhel, Mohammed A and Al-Amidie, Muthana and Farhan, Laith, Review of deep learning: Concepts, CNN architectures, challenges, applications, future directions, Journal of big Data, vol.
-8, pp.
-1-74, 2021
-\bibitem{12} Melekhov, Iaroslav and Kannala, Juho and Rahtu, Esa, Siamese network features for image matching, 2016 23rd International Conference on Pattern Recognition (ICPR), vol.
-1, pp.
-378-388, 2016, doi:10.1109/ICPR.2016.7899663
-
-\end{thebibliography}
 \end{document}

### 2022-05-21 paper.tex
Done image retrieval

@@
 This paper
-			then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspyred by curriculum learning, that helps reducing the training time. \\
+			then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspired by curriculum learning, that helps reducing the training time. \\
 			This is not the only work that uses neural networks to learn similarity, in fact there are also other application fields for similarity study.
@@
 \section{Data Collection}
-\section{Feature Extraction}
-\section{Prototype Construction}
-\section{Similarity Judgment}
 
-\section{Conclusion}
-\section{Possible Further Experiments}
+	\subsection{Image collection}
+		Since the proposed experiment uses neural networks, there is the need to have a lot of data.
+In this particular case, there is the need to gather many images.
+There are some image dataset, intended for computer
+		vision~\footnote{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}, that could help.
+Some of the dataset reported there are famous, like ImageNet or Google's Open Images.
+The
+		best for this kind of work, though, is to have a dataset that bases every image on the same ``macrocategory'', like for example a dataset made of images of birds.
+
+	\subsection{Typicaity values}
+
+%\section{Feature Extraction}
+%\section{Prototype Construction}
+%\section{Similarity Judgment}
+%\section{Conclusion}
+%\section{Possible Further Experiments}
 

### 2022-05-23 code_used_for_examples/cnn.py
Added some images, finished feature extraction section and began prototype construction

@@ -1,0 +1,66 @@
+import numpy as np
+from tensorflow import keras
+from keras import layers
+
+# Model / data parameters
+num_classes = 10
+input_shape = (28, 28, 1)
+
+# the data, split between train and test sets
+(x_train, y_train), (x_test, y_test) = keras.datasets.mnist.load_data()
+
+# Scale images to the [0, 1] range
+x_train = x_train.astype("float32") / 255
+x_test = x_test.astype("float32") / 255
+# Make sure images have shape (28, 28, 1)
+x_train = np.expand_dims(x_train, -1)
+x_test = np.expand_dims(x_test, -1)
+print("x_train shape:", x_train.shape)
+print(x_train.shape[0], "train samples")
+print(x_test.shape[0], "test samples")
+
+
+# convert class vectors to binary class matrices
+y_train = keras.utils.to_categorical(y_train, num_classes)
+y_test = keras.utils.to_categorical(y_test, num_classes)
+
+model = keras.Sequential(
+    [
+        keras.Input(shape=input_shape),
+        layers.Conv2D(32, kernel_size=(3, 3), activation="relu"),
+        layers.MaxPooling2D(pool_size=(2, 2)),
+        layers.Conv2D(64, kernel_size=(3, 3), activation="relu"),
+        layers.MaxPooling2D(pool_size=(2, 2)),
+        layers.Flatten(),
+        layers.Dropout(0.5),
+        layers.Dense(128, activation='relu'),
+        layers.Dense(64, activation='relu'),
+        layers.Dense(16, activation='relu', name='interesting_output'),
+        layers.Dense(num_classes, activation="softmax"),
+    ]
+)
+
+model.summary()
+
+batch_size = 128
+epochs = 15
+
+model.compile(loss="categorical_crossentropy", optimizer="adam", metrics=["accuracy"])
+
+model.fit(x_train, y_train, batch_size=batch_size, epochs=epochs, validation_split=0.1)
+
+score = model.evaluate(x_test, y_test, verbose=0)
+
+intermediate_layer_model = keras.Model( inputs=model.input,
+                                        outputs=model.get_layer('interesting_output').output)
+intermediate_output = intermediate_layer_model.predict(x_test)
+
+print("Test loss:", score[0])
+print("Test accuracy:", score[1])
+print(intermediate_output.shape)
+
+with open('intermediate_output.txt', 'w') as source:
+    source.write(np.array2string(intermediate_output))
+
+
+print(f'Extracted_features: {intermediate_output}')

### 2022-05-23 code_used_for_examples/color_histogram.py

@@ -1,0 +1,16 @@
+import cv2
+import numpy as np
+from matplotlib import pyplot as plt
+
+img = cv2.imread('imgs/obama.jpg')
+
+# Calculate histogram without mask
+hist1 = cv2.calcHist([img], [0], None, [256], [0, 256])
+hist2 = cv2.calcHist([img], [1], None, [256], [0, 256])
+hist3 = cv2.calcHist([img], [2], None, [256], [0, 256])
+
+plt.subplot(221), plt.imshow(img)
+plt.subplot(222), plt.plot(hist1), plt.plot(hist2), plt.plot(hist3)
+plt.xlim([0, 256])
+
+plt.show()

### 2022-05-23 code_used_for_examples/edge_extraction.py

@@ -1,0 +1,25 @@
+import cv2
+import os
+
+
+# Read the original image
+img = cv2.imread('imgs/obama.jpg')
+# Display original image
+cv2.imshow('Original', img)
+cv2.waitKey(0)
+
+# Convert to graycsale
+img_gray = cv2.cvtColor(img, cv2.COLOR_BGR2GRAY)
+# Blur the image for better edge detection
+img_blur = cv2.GaussianBlur(img_gray, (3, 3), 0)
+
+# Canny Edge Detection
+edges = cv2.Canny(image=img_blur, threshold1=100, threshold2=200) # Canny Edge Detection
+# Display Canny Edge Detection Image
+cv2.imshow('Canny Edge Detection', edges)
+cv2.waitKey(0)
+
+os.chdir('imgs')
+cv2.imwrite('obama_edges.jpg', edges)
+
+cv2.destroyAllWindows()

### 2022-05-23 code_used_for_examples/triangulation.py

@@ -1,0 +1,127 @@
+import os
+import cv2
+import numpy as np
+import random
+
+# Check if a point is inside a rectangle
+def rect_contains(rect, point) :
+    if point[0] < rect[0] :
+        return False
+    elif point[1] < rect[1] :
+        return False
+    elif point[0] > rect[2] :
+        return False
+    elif point[1] > rect[3] :
+        return False
+    return True
+
+# Draw a point
+def draw_point(img, p, color ) :
+    cv2.circle( img, p, 2, color, cv2.FILLED, cv2.LINE_AA, 0 )
+
+# Draw delaunay triangles
+def draw_delaunay(img, subdiv, delaunay_color ) :
+
+    triangleList = subdiv.getTriangleList()
+    size = img.shape
+    r = (0, 0, size[1], size[0])
+
+    for t in triangleList:
+
+        pt1 = (int(t[0]), int(t[1]))
+        pt2 = (int(t[2]), int(t[3]))
+        pt3 = (int(t[4]), int(t[5]))
+
+
+        if rect_contains(r, pt1) and rect_contains(r, pt2) and rect_contains(r, pt3) :
+
+            cv2.line(img, pt1, pt2, delaunay_color, 1, cv2.LINE_AA, 0)
+            cv2.line(img, pt2, pt3, delaunay_color, 1, cv2.LINE_AA, 0)
+            cv2.line(img, pt3, pt1, delaunay_color, 1, cv2.LINE_AA, 0)
+
+# Draw voronoi diagram
+def draw_voronoi(img, subdiv) :
+
+    ( facets, centers) = subdiv.getVoronoiFacetList([])
+
+    for i in range(0,len(facets)) :
+        ifacet_arr = []
+        for f in facets[i] :
+            ifacet_arr.append(f)
+
+        ifacet = np.array(ifacet_arr, np.int32)
+        color = (random.randint(0, 255), random.randint(0, 255), random.randint(0, 255))
+
+        cv2.fillConvexPoly(img, ifacet, color, cv2.LINE_AA, 0)
+        ifacets = np.array([ifacet])
+        cv2.polylines(img, ifacets, True, (0, 0, 0), 1, cv2.LINE_AA, 0)
+        cv2.circle(img, (int(centers[i][0]), int(centers[i][1])), 3, (0, 0, 0), cv2.FILLED, cv2.LINE_AA, 0)
+
+if __name__ == '__main__':
+
+    # Define window names
[…]

### 2022-05-25 paper.tex
First part of similarity learning, word count is 4526

--- 2022-05-20 paper.tex
@@
 \documentclass[conference]{IEEEtran}
-% \IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage[backend=biber, sorting=none]{biblatex}
+\usepackage{lipsum}
+\usepackage{url}
+\usepackage{subcaption}
+\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
 \addbibresource{bibliography.bib}
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
@@
 	\author{\IEEEauthorblockN{Samuel Kostadinov}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
 	\textit{University of Trento}\\
 	Trento, Italy \\
-samuel.kostadinov@unitn.it}
+	samuel.kostadinov@studenti.unitn.it}
 
@@
 
-	Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum
+		The typicality is a topic that still needs exploration.
+In this paper, the proposed experiment makes use of feature extraction to build a prototype and a siamese network to find a possible correlation
+		between the typicality of a concepts and the similarity between a given image and the built prototype.
 
@@
 
-	The typicality of a concept is a topic that needs a lot of exploration, since it's difficult to evaluate precisely the typicality of an object 
+		\noindent The typicality of a concept is a topic that needs a lot of exploration, since it's difficult to evaluate precisely the typicality of an object 
 		and also because the people's brains are always a little different from each other. The experiment I would like to propose, has the objective of 
-	make sure we can understand better the bond between the perceived typicality of an object that belongs to a category and the prototype of that category.
+		making us understand better the bond between the perceived typicality of an object that belongs to a category and the prototype of that category.
 		This can help the scientists to better understand how knowledge is organized in the brain. This experiment consists in different phases, such as
@@
 
-		Feature extraction is a topic widely studied. 
+			\noindent Feature extraction is a topic widely studied. 
 			This topic has numerous different applications. 
@@
 
-				After edge detection, other techniques began to spread for feature extraction. 
+					\begin{figure*}[!ht]
+						\centering
+						\begin{subfigure}[!ht]{0.48\linewidth}
+							\centerline{\includegraphics[width=0.9\linewidth]{imgs/obama.jpg}}
+							\label{fig:1a}
+						\end{subfigure}
+						\begin{subfigure}[!ht]{0.48\linewidth}
+							\centerline{\includegraphics[width=0.9\linewidth]{imgs/obama_edges.jpg}}
+							\label{fig:1a}
+						\end{subfigure}
+						\caption{Example of edge detection}
+						\label{fig:1}
+					\end{figure*}
+
+					\noindent After edge detection, other techniques began to spread for feature extraction. 
 					In a paper by Kumar and Kumar Bhatia written in 2014 \cite{kumar2014detailed}, 
@@
 
+				\begin{figure}[!ht]
+					\centerline{\includegraphics[width=\linewidth]{imgs/obama_histogram.png}}
+					\caption{Example of color histogram}
+					\label{fig:2}
+				\end{figure}
+
 				\subsubsection{Deformable shape analysis}
@@
 					update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
-				The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
+					The learning of the parameters can be seen as looking for the location with the highest.
+The matching problem is then fed to a statistical framework that computes the configuration minimizing the
 					energy cost, which corresponds to the best template match.
+
+					\begin{figure}[!ht]
+						\centerline{\includegraphics[height=0.4\textheight]{imgs/delaunay.jpg}}
+						\caption{Example of delaunay triangulation, the type of triangulation at the base of Felzenszwalb's paper}
+						\label{fig:3}
+					\end{figure}
 
@@
 
+					\begin{figure*}[!ht]
+						\centerline{\includegraphics[width=\linewidth]{imgs/cnn_features.png}}
+						\caption{Example of features extracted by a CNN}
+						\label{fig:4}
+					\end{figure*}
+
+					\noindent In Figure \ref{fig:4} there is an example of feature extracted by a Convolutional Neural Network.
+
 				\subsubsection{Hyperspectral images feature extraction}
 
-				Although there exists techniques that can extract features from hyperspectral images, this kind of images are created to capture the entire spectrum. This fact means that these images can capture 
-				more information then what the human eye can. techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent 
-				networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}.
-Probably, it's more meaningful to use normal images than these ones, since, as just
-
-			\subsubsection{Considerations about feature extraction}
-
-				Although there are different methods to extract feature, the ones that require neural networks are not easily understandable by humans. The classic feature extraction techniques have a more 
-				human comprehensible result, while the machine learning techniques extract feature in the form of vectors of attributes.
-Both of these can be used in the following steps, but the procedure requires
-				little adjustments in the steps based on the chosen procedure.
+					Although there exists techniques that can extract features from hyperspectral images, this kind of images are created to capture the entire spectrum.
+This fact means that these images can capture
+					more information then what the human eye can.
+techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent
+					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it's probably more meaningful to use normal 
+					images than these ones.
 
@@
 
-			Neural Networks are a powerful instrument in the hands of computer scientists.
+				\noindent Neural Networks are a powerful instrument in the hands of computer scientists.
 There exists a lot of different types of artificial neural networks, each with its own peculiarities.
@@
 
-				The applications of deep learning and CNNs are numerous. As shown previously, there are some CNNs used in image classification with the objective to identify diseases. The typical example is 
+					\noindent The applications of deep learning and CNNs are numerous.
+As shown previously, there are some CNNs used in image classification with the objective to identify diseases.
+The typical example is
 					the pneumonia detection. Another possibility is to use CNNs in segmentation or self driving cars, as stated in \cite{alzubaidi2021review} by Alzubaidi et al.
+
+					\begin{figure}[!ht]
+						\centerline{\includegraphics[width=\linewidth]{imgs/cnn_architecture.png}}
+						\caption{Example of CNN architecture. In particular, this image represents AlexNet's architecture}
+						\label{fig:5}
+					\end{figure}
+
+					\noindent In figure \ref{fig:5} there is an example of the architecture of a CNN, in particular AlexNet is the CNN chosen for this example.
 
@@
 					Siamese neural networks, also called twin networks, are a more recent advance in computer science. These neural networks have a different structure from convolutional neural networks. The 
-				structure of siamese neural networks is peculiar.
-In fact, there are two identical networks that process different inputs and, after that, merge in a single layer that measures the similarity between
+					structure of siamese neural networks is peculiar. In fact, there are two identical networks, called embedding networks, that process different inputs and, after that, 
+					merge in a single layer that measures the similarity between 
 					the two outputs of the two networks. The siamese neural networks have a different application compared to CNNs, in fact twin networks are mainly used to measure similarity of two objects. 
@@
 					paper, the objective is to find a similarity measure with a prototype.
+
+					\begin{figure}[!ht]
+						\centerline{\includegraphics[width=\linewidth]{imgs/siamese_architecture.png}}
+						\caption{Example of a Siamese Network architecture.}
+						\label{fig:6}
+					\end{figure}
+
+					\noindent In Figure \ref{fig:6} there is an example of a Siamese Neural Network, in particular the two embeddings are convolutional neural networks.
+
+					% Training with triplets (?)
 
@@
 This paper
-			then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspyred by curriculum learning, that helps reducing the training time. \\
+				then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspired by curriculum learning, that helps reducing the training time. \\
 				This is not the only work that uses neural networks to learn similarity, in fact there are also other application fields for similarity study.
@@
 	\section{Data Collection}
-\section{Feature Extraction}
-\section{Prototype Construction}
-\section{Similarity Judgment}
+
+		\subsection{Image collection}
+
+			\noindent Since the proposed experiment uses neural networks, there is the need to have a lot of data.
+In this particular case, there is the need to gather many images.
+There are some image dataset, intended for computer
+			vision~\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help.
+Some of the dataset reported there are famous, like ImageNet or Google's Open Images.
+The
+			best for this kind of work, though, is to have a dataset that bases every image on the same ``macro-category'', like for example a dataset made of images of birds.
+
+		\subsection{Typicality values}
+
+			\noindent In this experiment, typicality judgments play a crucial role.
+To gather enough data about the perceived typicality of images, a form is necessary.
+This survey should be structured in a way that presents an
+			image ad a time to the subject that is taking the survey and asks to rate the typicality of the object portrayed in the image, possibly in a given range.
+If that's the case, a range between $1$ and $10$
+			could be the best decision since people are quite used to rate in this range. Once there are enough results, the various rates should be averaged so that there is a single measure that takes into 
+			account every rate taken from the survey. The number of people that should participate in the experiment should be high enough to be a meaningful statistical group.
+
+	\section{Feature Extraction\label{sec:fe}}
+
+		\noindent While collecting the needed data with the survey, it's possible to begin the feature extraction procedure.
+There are various possibilities for this step, as shown in the Section dedicated to feature extraction background.
+		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient.
+Since feature extraction has already been described in the paper, this section will
+		present a discussion about the results of the presented methods' results. The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
+		In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process.
+For example, in edge extraction, humans have no difficulty in recognizing if the
+		edge extracted is correct or not seeing the original image.
+For example, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left,
+		while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
+		Moreover, classical and machine learning features can give different weights to different features. 
+		In fact, classical methods rely on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works.
+An empirical confirmation of this fact
+		can be that if a person asks to another person to describe, for example, a common kingfisher, the person that should describe the bird will, most likely, start describing the dimension, the shape, and only
+		later the colour.
+Machine learning techniques, on the other hand, could give a very high importance to the fact that the bird is mainly blue and red, if they have access to the colour information.
+Due to the fact that
+		the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to
+		shape-related features.
+
+	\section{Prototype construction}
+
+		\noindent The construction of the prototype is one of the most delicate parts of the experiments. How this phase works depends heavily on what method was used for feature extraction.
+
+		\subsection{Classical feature extraction techniques}
+
+			\noindent In case classical feature extraction techniques were used, the goal of this activity is to build an image that presents in itself a ``prototype'' of the object.
+For example, a prototype of a bird, could be
+			an imaginary bird with a shape that it's obtained with a weighted average of the shapes of all the birds in the image. For example, since a birds like sparrows and swallows are perceived as more 
+			typical than ostriches and penguins the prototype should resemble more swallows and sparrows than ostriches and penguins. To do so, the key factor is performing numerous analyses on various 
+			different subjects, until there are enough data to have a statistical value.
+
+			\begin{figure*}[!t]
+				\centering
+				\begin{subfigure}[!t]{0.48\linewidth}
+					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
+				\end{subfigure}
+				\begin{subfigure}[!t]{0.48\linewidth}
+					\centerline{\includegraphics[height=0.4\textheight]{imgs/penguin_edges.jpg}}
+				\end{subfigure}
+				\caption{Edge extraction of swallow and penguin}
+				\label{fig:7}
+			\end{figure*}
+
+		\noindent In Figure \ref{fig:7} there is an example of the edges of two different birds. Although both of the subjects of the original 
+		subjects are birds, one is much more typical than the other one.
+In this case, the prototype should try to match more the swallow edge than the penguin edge.
+A way to do so could make use deformable
+		template matching.
+Matching a shape with a template could be useful to find a weighted average between the two shapes.
+In this way, the resulting shape takes into account both the original edges while
+		giving priority to the one more typical.
+		This procedure should be applied for both shape features and colour features, so that all the features that can be extracted from the prototype image resemble the weighted average of all the feature from
+		the original images.
+
+		\subsection{Machine learning feature extraction techniques}
+
+			\noindent In case machine learning feature extraction techniques were used, it's conceptually and practically easier to compute the average features.
+In fact, the features extracted by machine learning techniques are
+			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors.
+
+		\subsection{Considerations about prototype construction}
+
+			\noindent The prototype depends on the feature extraction technique that was used.
+As discussed in Section \ref{sec:fe}, the key difference is human interpretability.
+In fact, building a prototype using the
+			classical feature extraction methods, results in an image that can be seen and interpreted. Using a prototype generated with machine learning feature extraction techniques results in an array 
+			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
+			a work by Carvalho written in 2019, %(\textbf{SOME CITATIONS}),
+			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the european union in the field of artificial intelligence.
+In particular, there is a document of
+			the act~\footnote{\url{https://eur-lex.europa.eu/resource.html?uri=cellar:e0649735-a372-11eb-9585-01aa75ed71a1.0001.02/DOC_1&format=PDF}} that states that there will be some requirements in terms of
+			transparency and intepretability for machine learning systems that are considered high-risk AI.
+The growing interest produced some results, but still they're not enough to easily interpret machine learning
+			features.\\
+			Most likely, in the future will be possible to look at the features extracted by a neural network and comprehend their meaning.
+When this will be possible, independently of the feature extraction techniques
+			used, the human interpretability will be possible, and with that in mind it would be probably more convenient to extract the features using neural networks. The reason behind this consideration is 
+			that although the training of a neural network can be expensive in computational terms, the evaluation of an input on a trained network it's not very computationally demanding.
+On the other side, algorithms
+			like the triangulation always have the same demand, that is lower than the demand of training a neural network, but surely higher than the demand of evaluating a single input on a neural network. 
+			Moreover, considering the possiblity to use transfer learning techniques, the training can become a fine-tuning or a domain adaptation, which means the computational load is lighter.
+Considering that
+			the fact that the training is a demanding task to be perfomed only once and that other algorithms may be less demanding but must be run multiple times, it's probably more convenient to train a neural
+			network.
+Moreover, not only the feature extraction process is convenient, but also the prototype construction itself is more convenient if the features are in the form of numerical parameters, since it's
+			enough to perform a weighted average, a simpler operation if confronted with the construction of a new image that should take into account features of numerous other images.
+
+	\section{Similarity learning}
+
+		\noindent The similarity learning is the core part of the experiment.
+In this experiment, the similarity learning is done through a siamese neural network but, as the previous steps, its architecture depends on the
+		feature extraction techniques used.
+
+		\subsection{Classic feature extraction techniques}
+
+			\noindent If the feature extraction process happened with classical techniques, after the prototype building step the result is an image.
+This means that the two embedding networks must be able to process
+			images. Most likely, the best choice, in this case, is to implement two CNNs as embedding networks and merge them in a single fully connected network for the siamese similarity learning. 
+			In this case, the siamese network would be fed the prototype image and the an image from the dataset.
+The goal of this kind of prediction is to learn a similarity metric with some annotated values.
+			After learning the similarity metric, the network will be able to measure the similarity of the prototype image and any other image fed in the other embedding network.
+By doing so and retrieving various
+			measurements the couple of values \textit{perceived typicality - similarity measure} could reveal some interesting patterns.
+
+		\subsection{Classic feature extraction techniques}
+
+			\noindent If the feature extraction process involved neural networks, after the prototype building step the result is not anymore an image but it's a vector of values.
+This implies that there is no need to
+			use a convolutional neural network as embedding, but it's enough to have some fully connected layers that will be merged in a single fully connected network for the similarity learning.
+The rest of the procedure
+			is similar, since the siamese network will still be fed the features of the prototype and the features of an imaage of the dataset.
+
+		\subsection{Loss function}
+
+			\noindent The loss function is a key factor of this kind of leaning, togheter with the distance measure.
+In fact, siamese neural networks usually use a loss function that is called contrastive loss.
+This kind
+			of loss is based on a distance measure that should be defined by the person doing the experiment.
+The type of measure that it's possible to use ranges a lot, from simple distances like the manhattan distance
+			or the euclidean distance to more complex measures that can be defined by the user.
+
+		% Word count without this section: 4526
+		\subsection{Considerations about similarity learning}
+
+			% 
+			\noindent
+
+	\section{Possible Further Experiments\label{sec:pfe}}
+
+		\subsection{Possible variants in similarity learning}
+
+		\subsection{Possible relevant follow-ups of similarity learning}
 
 	\section{Conclusion}
-\section{Possible Further Experiments}
 

### 2022-05-29 paper.tex
Doing things in no particular order

@@
 		making us understand better the bond between the perceived typicality of an object that belongs to a category and the prototype of that category.
-		This can help the scientists to better understand how knowledge is organized in the brain. This experiment consists in different phases, such as
-		data collection, feature extraction, prototype construction and similarity judgment.
+		This experiment consists in different phases, such as data collection, feature extraction, prototype construction and similarity judgment.
+
+	\section{Applications}
+
+		\noindent The possible applications of this experiment are widely ranged. First of all, this experiment could help neuroscientists understand how the knowledge is 
+		organized in the brain. By doing so, there is the possibility to increase the knowledge about the brain and how it works. Moreover, it's possible to confront 
+		the way that a person with cognitive disorders or, more generally, some kind of mental disorder related to knowledge with the results of people without 
+		any disorder, trying to understand if the way that knowledge is handled in the brain is somehow similar or completely different. Lastly, this experiment can 
+		also help to understand if knowledge is encoded in a similar way in artificial and biological neural systems.
 
 	\section{Background}
+
+		\subsection{Typicality}
+
+			\noindent Typicality is one of the key concepts that will be used in this paper, so it's fundamental that it's defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
+			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
+			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, in this paper, defined  a measure of how representative an example is of their category and 
+			of the other members of the same category.
 
@@
 					\centerline{\includegraphics[width=\linewidth]{imgs/obama_histogram.png}}
-					\caption{Example of color histogram}
+					\caption{Color histogram of the image used in \ref{fig:1}}
 					\label{fig:2}
@@
 					first one is preprocessing, the second is feature extraction and the third is brain tumour classification.
-The first step is just to rescale the values to the range $[0,\ 1]$.
+The first step is just to rescale the values to the range $[0,1]$.
 The feature extractor
@@
 			vision~\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help.
-Some of the dataset reported there are famous, like ImageNet or Google's Open Images.
+Some of the dataset reported there are quite famous, like ImageNet or Google's Open Images.
 The
 			best for this kind of work, though, is to have a dataset that bases every image on the same ``macro-category'', like for example a dataset made of images of birds.
+Even though this is the ideal case,
+			most of the dataset that are used for computer vision contain more than one single category.
+For example, ImageNet, which is one of the most famous image datasets, contains more than 1 million images that are divided
+			into 1000 classes. Generally, it's possible to use these datasets, which have different macro categories by filtering the input images based on the macro category the experiment is based on.
 
-		\subsection{Typicality values}
+		\subsection{Typicality values\label{sec:typval}}
 
@@
 This survey should be structured in a way that presents an
-			image ad a time to the subject that is taking the survey and asks to rate the typicality of the object portrayed in the image, possibly in a given range.
+			image at a time to the subject that is taking the survey and asks to rate the typicality of the object portrayed in the image, possibly in a given range.
 If that's the case, a range between $1$ and $10$
@@
 			account every rate taken from the survey. The number of people that should participate in the experiment should be high enough to be a meaningful statistical group.
+
+		\subsection{Possible alternative to typicality values\label{sec:patv}}
+
+			Another possibility to gather data, it's to ask people to list a certain number of objects or all the objects they can think about of the decided category.
+For example, let's assume the macro category decided
+			is ``birds''.
+It's possible to collect enough data by asking people to list a the first few examples of birds, using a predefined number.
+Moreover, it's possible to use a variant of this procedure and ask people
+			to list all the examples of birds that they can think of.
+These two variants of the same data collection approach are both possible and come with some advantages and disadvantages when compared to the other
+			method described in \ref{sec:typval}.
+% In case this type of data collection is used, the values of typicality should be also a question that asks the subjects to describe all the features that birds have in common
+			% with each other. This step will then be used for prototype construction.
+
+		\subsection{Considerations about the survey}
+
+			The two presented methods proposed for data collection are very different.
+Both of these have their own pros and cons.
+The first method can help in having a typicality value for every image collected in the dataset,
+			while the second does not.
+The large number of images that should be used, though, it's not feasible to ask the subjects to rate the typicality value of all the images of the dataset.
+In fact, it's very likely
+			that a subject that has to rate the typicality of a large number of images will be tired after a certain number of images, polluting the results of the survey.
+A possible solution to this problem is to
+			divide the survey so that subjects have to rate the typicality of a limited number of images.
+This method would result in a lower amount of data, but at the same time, a more precise amount of data.
+Another
+			problem with this method it's that it has a possible bias.
+In fact, if a person sees a bird, for example a swan, or a duck, and is asked to rate its typicality, most likely will rate it in the higher part
+			of the scale, while if asked to list a certain number of birds it's more likely that it's not present than that it's present.\\
+			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject didn't think of.
+			Recalling the previous example with the swan, if a person does not think of the swan, it won't be present in the list created by the subject.
+This could result in a lower bias, but it comes at the cost
+			of having to interview more people and, most likely, not having enough data for some of the examples.
+In this approach, the more a bird is typical, the more it appears in the lists and in higher positions.
+			There is an example in the appendix.
+Even though this method has the advantage of having less bias, has a  great drawback.
+That is, in particular, the fact that the prototype construction is very difficult.\\
+			In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two
+			methods and decide which one is more convenient.
+			As alternative, it's possible to try both the methods and see which one gives better results.
+In this way, both the possibilities will be used and there is the possibility to see which one is better in
+			terms of performance.
 
@@
 		Moreover, classical and machine learning features can give different weights to different features. 
-		In fact, classical methods rely on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works.
+		In fact, classical methods rely mostly on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works.
 An empirical confirmation of this fact
@@
 		the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to
-		shape-related features.
+		shape-related features.	\\
+		If the data collection method chosen is the one that asks people to list the objects of the category, the feature extraction can happen in two possible ways.
+The first way is to use the data collected for
+		typicality judgments and collect also images of the birds that appear in the results. After collecting enough images, the feature extraction process can proceed as described earlier and use either  
+		classical or machine-learning-based feature extraction methods.
+Although this is a possibility, there could be an alternative.
+The alternative seems interesting because it can be adapted to rely only on features
+		that humans identify as important.
+To do so, the survey should include a question that asks the subjects to list all the characteristics that the objects of the given macro category have in common.
+In this case,
+		the features are not strictly extracted by the dataset, but are listed by the subjects that take part in the survey.
+By doing so, the experiment takes into account, in the prototype, only the features that
+		human have listed, so only the features that are considered important by humans themselves.
+Although it's theoretically possible, this procedure will result in numerous complication in prototype construction.
 
@@
 			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors. 
+			%Allungare (?)
 
-		\subsection{Considerations about prototype construction}
+		\subsection{Other survey method}
+
+			%Diificile, da pensare bene.
+
+		\subsection{Considerations about prototype construction\label{sec:cpc}}
 
@@
 			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
-			a work by Carvalho written in 2019, %(\textbf{SOME CITATIONS}),
+			a work by Carvalho written in 2019~\cite{electronics8080832}, %(\textbf{SOME CITATIONS}),
 			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the european union in the field of artificial intelligence.
@@
 
-		\noindent The similarity learning is the core part of the experiment.
-In this experiment, the similarity learning is done through a siamese neural network but, as the previous steps, its architecture depends on the
+		\noindent The similarity learning is the core part of the experiment. In this experiment, the similarity learning is done through a siamese neural network but, as the previous steps, depends on the 
 		feature extraction techniques used.
@@
 This means that the two embedding networks must be able to process
-			images. Most likely, the best choice, in this case, is to implement two CNNs as embedding networks and merge them in a single fully connected network for the siamese similarity learning. 
-			In this case, the siamese network would be fed the prototype image and the an image from the dataset.
-The goal of this kind of prediction is to learn a similarity metric with some annotated values.
+			images. Most likely the best choice, in this case, is to implement two CNNs as embedding networks and merge them in a single fully connected network for the siamese similarity learning. 
+			In this case, the siamese network would be fed the prototype image and an image from the dataset. The goal of this kind of prediction is to learn a similarity metric with some annotated values. 
 			After learning the similarity metric, the network will be able to measure the similarity of the prototype image and any other image fed in the other embedding network.
@@
 
-		\subsection{Classic feature extraction techniques}
+		\subsection{Machine learning feature extraction techniques}
 
@@
 			is similar, since the siamese network will still be fed the features of the prototype and the features of an imaage of the dataset.
+As in the previous case, the goal of this kind of prediction is to learn
+			a similarity metric using annotated values. After learning the metric, the network will be able to measure the similarity of the prototype and any other image. 
+			By doing so the couple of values \textit{perceived typicality - similarity measure} could reveal some interesting patterns.
 
@@
 
-			\noindent The loss function is a key factor of this kind of leaning, togheter with the distance measure.
+			\noindent The loss function is a key factor of this kind of leaning, together with the distance measure.
 In fact, siamese neural networks usually use a loss function that is called contrastive loss.
 This kind
-			of loss is based on a distance measure that should be defined by the person doing the experiment.
-The type of measure that it's possible to use ranges a lot, from simple distances like the manhattan distance
+			of loss is based on a distance measure that should be defined by who is conducting the experiment.
+The type of measure that it's possible to use ranges a lot, from simple distances like the Manhattan distance
 			or the euclidean distance to more complex measures that can be defined by the user.
 
-		% Word count without this section: 4526
-		\subsection{Considerations about similarity learning}
+		\subsection{Considerations about similarity learning\label{sec:csl}}
 
-			% 
-			\noindent
+			\noindent The two possible embedding networks, convolutional and fully connected, lead to different internal results but the final goal is the same.
+In fact, even if with different computations, the siamese
+			network outputs a similarity measure.
+This output strongly relies on the distance measure.
+In fact, the same two vectors can have different similarity measures, based on the type of distance that the user
+			decided to implement. For example, suppose that the vectors are $[2,\ 3]$ and $[5, 8]$. If the Manhattan distance is chosen as measure, the distance between the two defined vectors is $8$. 
+			Using the euclidean distance instead of the Manhattan distance, the result is $~5,83$.
+In data science there are some possibilities for distance measurements, a part from euclidean and Manhattan distance.
+Some
+			examples are the cosine distance or the Hamming distance.
+Moreover, there could be an ad hoc distance measure, defined for this problem in order to optimize the results obtained by the neural network.
+			This kind of freedom is very beneficial, since it gives the possibility to use different formulas and, seeing the results, there is also the possibility to see which distance works better.
+This could give an
+			insight on which one of the distance measures is the closest to the one used by human brain in similarity judgement. \\
+			Focusing more on the computational aspect of the similarity learning, the more convenient approach is the one involving neural networks feature extraction.
+In fact, if the features are extracted with
+			neural networks, the siamese network will only need fully connected layers, while it would need convolutional, pooling and fully connected layers if the features are extracted with in a classical way.
+			The only problem about the machine learning feature extraction techniques is, as mentioned in \ref{sec:cpc}, is the fact that we're still unable to interpret the features extracted by a CNN.
 
-	\section{Possible Further Experiments\label{sec:pfe}}
+	\section{Possible Further Experiments}
 
@@
 
-		\subsection{Possible relevant follow-ups of similarity learning}
+			\noindent The siamese network described in \ref{sec:csl} has no constraints about both the distance measure and the loss function.
+An interesting possibility could be using a distance measure that is sensitive
+			to human similarity judgments. In this way, the network will optimize the weights in order to predict based on the human similarity measure. The resulting similarity measure can be, in this case, 
+			compared with the state-of-art human similarity judgments obtained with CNNs.\\
+			Another possibility is to adopt a variant of the previously described network.
+For example, it's possible to use a variant of siamese neural networks that uses triplets for training.
+In this version,
+			the network takes in input a reference (which is the prototype in the case of this experiment) and two values, one positive and one negative.
+The network tries to maximize the distance between the reference and
+			the negative example, while minimizing the distance between the reference and the positive example.
+There is a way, as shown by Dor et al.
+in \cite{ein-dor-etal-2018-learning}, to adapt the triplet
+			network to learn a similarity metric.
+In this way, the similarity metric is learned and so the network itself tries to optimize it.
+There are different research papers that show how triplet networks
+			usually outperform siamese networks, especially in one-shot learning.
+Could be interesting, in this experiment, to confront both siamese neural networks and triplet networks to see which performs better.
+			Moreover, this could give some hints on how the human similarity judgments work.
+
+		\subsection{Possible relevant experiments}
+
+			\noindent One of the first ideas that is an interesting follow-up of this experiment is to compare the results obtained with the two possible feature extraction methods.
+Even though one of the two methods is not
+			interpretable by humans, it's still interesting trying to understand which of the methods is more efficient in detecting features relevant for the similarity learning. Moreover, if the results 
+			indicate that the machine learning techniques are more efficient, could be a push in the research that try to understand the neural networks' feature extraction method. This could be interesting 
+			for the future of neural networks and neuroscience. \\
+			After the described experiment, there are some natural extensions of the experiment.
+One of the most natural and obvious extensions of the experiment is to try the same experiment with another category
+			of images.
+For example, if the first experiment is conducted on a dataset with bird images, it could be interesting to conduct the same experiment on a dataset that uses a different animal, like, for
+			example, fishes.\\
+			Another experiment that comes as natural is trying to apply some transfer learning techniques. This could be interesting because, as far as we know, the human brain similarity can work 
+			in different ways in judging similarity of different images.
+Applying transfer learning, we could see if the feature extracted for a category are also effective for a different category.
+This can give
+			extra insight about the typicality and its perception and how it works in human brain.
+The results can show that human brain innately use the same kind of measure of typicality or a different measure of
+			typicality for different classes.
+Of course, either result should be investigated more, since a single test is not enough to prove that one of the two possibilities is more likely than the other.
+Even though
+			it's not enough for a proof, could be an interesting starting point for neuroscientists to better understand how typicality works in human brain.\\
+			Another possibly interesting topic could be examining the results of the survey based on the region of the person answering.
+In fact, it's possible that different regions, that have slightly different
+			cultures and that may result in slightly different typicality perception.
+For example, in Europe the eagles are not common, so it's very likely that people will give a high typicality to eagles, while
+			in North America, since the bald eagle is a national symbol, it's easier that people associate with it a higher typicality value. Moreover, there are a lot of different factors that can influence 
+			the typicality rates of images in people.
+For example, a farmer could be more inclined than people that live in a big city to think associate a chicken with the concept of ``bird'', and thus giving
+			it a higher typicality.\\
+			Lastly, it's worth notice that in this paper the prototype is considered as the mean of the features extracted from all the the images of the dataset.
+A possibility that could be interesting would be
+			interesting to try to experiment the possibility to use different concept of prototype and implementing the correspondent methods of building it.\\
+			% Cognitive/learning disorders (?)
 
 	\section{Conclusion}
+
+		The experiment proposed has the objective to help identifying, if it exists, a link between the typicality of a concept and the similarity to a prototype.
+The work strongly relies on neural networks, in
+		particular siamese networks, and using them tries to achieve the goal of linking similarity of a prototype with the typicality.
+Both if the siamese network can achieve good statistics or if it cannot achieve
+		good statistics, the result can give an idea of the correlation between typicality and a prototype of a concept.
+
+	\appendix
+
+	\section{Appendix\label{sec:app}}
+
+		To test the method of data collection described in \ref{sec:patv}, I collected the results of a small survey in which there were 10 questions, each asking to give the name of a bird. The number of 
+		people that answered is not big enough to be a statistically relevant group, since the number of the answers is only $14$.
+
+		\begin{figure*}
+			\centerline{\includegraphics[width=\linewidth]{imgs/survey_hist.png}}
+			\caption{Results of the survey}
+			\label{fig:app}
+		\end{figure*}
+
+		\noindent In Figure \ref{fig:app} there are the results of the survey. Even though the number of answers was not very big, some problems were still emerged.
+		\begin{itemize}
+
+			\item \textbf{Off-topic answers or blank answers}:
+
+				\noindent In this case, one of the answers had to be deleted from the answers, since the cited example was not part of the category decided for the survey.
+In particular, the survey asked for examples of birds,
+				while one of the answers was ``gazelle''. This fact highlights a problem bound to the number of examples the user knows or can think of. In this example, the survey asked for $10$ names of birds,
+				which I thought was a reasonable number, but probably some of the subjects that took part to this survey could not think of a $10^{th}$ name, so just put a name of another animal. The solution 
+				to this problem is to apply some data cleaning to the answers to filter the examples that, eventually, are in the answers but not part of the given category.
+An analogue approach can be applied if the
+				subject leaves the answer blank for the same reason.
+
+			\item \textbf{Capitalization of examples}:
+
+				\noindent This problem is simpler than the previous one to solve, since it just involves the capitalization of the answers.
+If the survey starts accounting numerous results, it becomes difficult to
+				compute the number of times that a particular example appears in the answers, so, most likely, there will be some automated scripts that compute all the needed statistics.
+This could be a problem since
+				in most of the programming languages, if not all, words like ``Robin'' and ``robin'' are considered different based on the capitalization. This problem is easily solvable by lowercasing all the 
+				answers.
+
+			\item \textbf{Typos of examples}:
+
+				\noindent This problem can be quite challenging to solve.
+In fact, subjects could make some mistakes when typing the answers, so for example a word like ``robin'' can become ``ribin'' or ``tobin'' for example.
+				Moreover, if more than one letter is wrong, some results like ``rivim'' instead of ``robin'' are possible, especially if the subjects compile the form via mobile devices. To solve this issue, 
+				it's possible to use some distance between strings, like for example the Levenshtein distance, which is frequently used to find the distance between two strings. Although this could be a solution,
+				it's not guaranteed that the result is correct, so these results should always be checked again to prove they are correct and, most importantly, coherent with the category the survey is based on.
+
+			\item \textbf{Different specificity levels}:
+
+				\noindent This problem is very difficult to overcome.
+There is an example in the histogram reported as results.
+In the histogram, in fact, it's possible to note that there are both the ``eagle'' and
+				the ``bald eagle'' labels. This means that different subjects can answer with different levels of specificity, since the ``eagle'' label is more general than its counterpart ``bald eagle''. 
+				This problem is presented also in an inter-species context, for example the ``Common kingfisher'' represents a single specie, representative of the ``kingfisher'' genus, while, for example, 
+				``Flamingo'' represents a family, of which some examples are the greater flamingo and the lesser flamingo, along with other species as well. 
+				Even though the problem is very clear, it's not very clear what to do in this case. A possibility is to decide that, in this case, the ``bald eagle'' label should be incorporated in the ``eagle'' 
+				label, making sure that all the instances of the most specific one are accounted as instances of the more general one. Another possibility is to keep both of the labels, so that the results of 
+				the survey are unaltered. Lastly, it's possible to assume that every label that identifies a group more general than a single specie, like a family or a whole order is referred to the most 
+				common specie of that family or order. The only way to know exactly which of these possibilities performs better is conducting some experiments and compare the obtained results.
+
+		\end{itemize}
+
+		\noindent Even with all these problems, the survey works quite well, since also with a few answers the results show that most of the subjects had mentioned the most common birds, like pigeons, while the
+		less common ones, like for examples peacocks, are mentioned fewer times.
+The results of this particular survey show that, a part for some examples, most of the birds appear only a few times.
+Although there
+		are some examples that are most likely outliers even with large numbers of subjects taking the survey, like ``Dodo'', some other examples, like ``Swift'' or ``Common blackbird'', 
+		are likely to be more typical with a larger number of people taking the survey.\\
+		The goal of the survey is to infer a measure of typicality based on how often a certain example appears in the results of the answers, and the result, at first glance, seems to be achieved.
+Although only
+		a test can prove this, it's very likely that with a larger group of subjects taking the survey, the results will differ more than with a small number of subjects.
+
+	\newpage
 

### 2022-05-29 code_used_for_examples/survey.py

@@ -1,0 +1,43 @@
+from collections import Counter
+import matplotlib.pyplot as plt
+
+
+ans_1 = ['robin', 'robin', 'robin', 'pigeon', 'pigeon', 'Great tit', 'eagle', 'pigeon', 'wren', 'Common nightingale',
+         'magpie', 'sparrow', 'common blackbird ', 'parrot']
+ans_2 = ['flamingo', 'flamingo', 'Heron', 'common cuckoo', 'canary', 'skylark', 'robin', 'pigeon', 'dove', 'swift',
+         'Hummingbird', 'Common nightingale', 'crow', 'common kingfisher']
+ans_3 = ['pigeon', 'pigeon', 'penguin', 'hoopoe', 'canary', 'dove', 'Hummingbird', 'robin', 'dove', 'Seagull',
+         'parrot', 'crow', 'common blackbird ', 'partridge']
+ans_4 = ['robin', 'robin', 'Seagull', 'Seagull', 'pigeon', 'swift', 'penguin', 'peacock', 'hoopoe', 'owl of Athena',
+         'quail', 'great spotted woodpecker', 'swift', 'parrot']
+ans_5 = ['eagle', 'Great tit', 'white stork', 'magpie', 'Hawk', 'chicken', 'Condor', 'goldfinch', 'pigeon', 'robin',
+         'dove', 'swift', 'crow', 'owl']
+ans_6 = ['Hawk', 'Hawk', 'common cuckoo', 'common cuckoo', 'Hummingbird', 'Hummingbird', 'eagle', 'magpie', 'crow',
+         'common kingfisher', 'sparrow', 'owl of Athena', 'canary', 'common blackbird']
+ans_7 = ['dove', 'dove', 'common blackbird', 'common blackbird', 'eagle', 'pigeon', 'Seagull', 'Ibis', 'toucan',
+         'magpie', 'Woodpecker', 'Hawk', 'Common nightingale', 'eagle']
+ans_8 = ['white stork', 'owl', 'magpie', 'Hawk', 'goldfinch', 'swift ', 'sparrow', 'sparrow', 'crow',
+         'Common nightingale', 'kite', 'owl of Athena', 'dove', 'parrot']
+ans_9 = ['robin', 'robin', 'eagle', 'common chaffinch', 'bald eagle', 'owl', 'chicken', 'Albatross',
[…]

### 2022-06-04 paper.tex
Finished

@@
 \usepackage[backend=biber, sorting=none]{biblatex}
-\usepackage{lipsum}
 \usepackage{url}
@@
 		the way that a person with cognitive disorders or, more generally, some kind of mental disorder related to knowledge with the results of people without 
-		any disorder, trying to understand if the way that knowledge is handled in the brain is somehow similar or completely different. Lastly, this experiment can 
+		any disorder, trying to understand if the way that knowledge is organized in the brain is similar or completely different. Lastly, this experiment can 
 		also help to understand if knowledge is encoded in a similar way in artificial and biological neural systems.
@@
 			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
-			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, in this paper, defined  a measure of how representative an example is of their category and 
-			of the other members of the same category.
+			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, as defined in this paper, a measure of how representative 
+			an example is of their category and of the other members of the same category.
 
-		\subsection{Feature extraction}
+		\subsection{Feature extraction\label{sec:bfe}}
 
 			\noindent Feature extraction is a topic widely studied. 
-			This topic has numerous different applications. 
+			This topic has numerous applications. 
 			One of its goals is to reduce the amount of computational power needed for image processing. 
@@
 					Some examples are the Sobel operator and the Canny edge detector. 
-					Each of the methods has pros and cons. 
-					It's the user's job to find the most appropriate for its goal~\cite{owotogbe2019edge}.\\
+					Each algorithm has its own peculiarities and it's the user's job to find 
+					the most appropriate for its goal~\cite{owotogbe2019edge}.\\
 
@@
 							The Fourier transform is commonly used for shape analysis. 
-							The Fourier transformed coefficient form the Fourier descriptors. 
+							The transformed coefficient are called the Fourier descriptors.
 							These descriptors represent the shape in a frequency domain, with the low frequencies symbolizing the general shape and the high frequencies symbolizing details of the shape. 
@@
 This type of representation lets approximate every 2D shape without holes using a representation based on triangles.
-					%The resulting approximation is as precise as the user decides, meaning that it's very flexible for the representation of shapes. 
-					%In particular, in the paper the triangulation was done with a technique called constrained Delaunay triangulation (CDT), because of its tight relation with the medial axis transform. 
 					The author also make use of the properties of chordal graphs and k-trees.\\
@@
 The objective is to find the transformation with the lowest possible cost.
-This component is very flexible, since depending on the formulation of the energy function the costs
+This component is very flexible, since, depending on the formulation of the energy function, the costs
 					can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
-					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually requires an initialization near to the correct solution, 
+					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually require an initialization near to the correct solution, 
 					although this is not required for the algorithm presented in this paper. 
-					For the implementation of the algorithm itself, a techniques called non-serial dynamic programming was the key factor.
+					For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor.
 In fact, using the order of perfect elimination (property of the every triangulated
@@
 						\centerline{\includegraphics[height=0.4\textheight]{imgs/delaunay.jpg}}
-						\caption{Example of delaunay triangulation, the type of triangulation at the base of Felzenszwalb's paper}
+						\caption{Example of Delaunay triangulation, the type of triangulation at the base of Felzenszwalb's paper}
 						\label{fig:3}
@@
 that proposes another method~\cite{varshni2019pneumonia}.
-This paper has the objective to classify images suing CNNs to understand if a patient
+This paper has the objective to classify images using CNNs to understand if a patient
 					has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
@@
 					more information then what the human eye can.
-techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent
+The techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent
 					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it's probably more meaningful to use normal 
@@
 
-				\subsubsection{Convolutional Neural Network (CNN)}
+				\subsubsection{Convolutional Neural Networks (CNN)}
 
@@
 These networks use mostly three kind of layers: Dense layers (which are fully connected layers),
-					convolution layers and pooling layers. In the following, there will be a short description of each kind of layer. 
+					Convolutional layers and Pooling layers. In the following, there will be a short description of each kind of layer. 
 					\begin{itemize}
@@
 
-				\subsubsection{Siamese Neural Network}
+				\subsubsection{Siamese Neural Networks}
 
@@
 					structure of siamese neural networks is peculiar. In fact, there are two identical networks, called embedding networks, that process different inputs and, after that, 
-					merge in a single layer that measures the similarity between 
+					they merge in a single layer that measures the similarity between 
 					the two outputs of the two networks. The siamese neural networks have a different application compared to CNNs, in fact twin networks are mainly used to measure similarity of two objects. 
 					In the case of this paper, the siamese neural networks are used for image matching.
-This is not the first time that siamese networks are used for image matching, as proved by a paper written in 2016 by
+This is not the first time that siamese networks are used for image matching, as shown in a paper written in 2016 by
 					Melekhov et al.~\cite{melekhov2016siamese}, but with a little difference in the objective of the matching.
@@
 
-					% Training with triplets (?)
-
 			\subsection{Similarity judgments}
 
-				In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017~\cite{appalaraju2017image}.
+				\noindent In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017~\cite{appalaraju2017image}.
 In this work they explore the possibility to
@@
 				learning the actual similarity measure, the authors processed the input through a CNN and performed a step they call ``Time fusion''. This step let them incorporate the time information and 
-				weight differently eventual symptoms based on their temporal distance from the onset of the disease. Only after this step the authors proceeded to learn a similarity metric, basing the learning 
+				weight differently eventual symptoms based on their temporal distance from the first appearance of the disease.
+Only after this step the authors proceeded to learn a similarity metric, basing the learning
 				on CNNs.\\
@@
 There are some image dataset, intended for computer
-			vision~\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help.
+			vision\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help.
 Some of the dataset reported there are quite famous, like ImageNet or Google's Open Images.
 The
-			best for this kind of work, though, is to have a dataset that bases every image on the same ``macro-category'', like for example a dataset made of images of birds.
+			best for this kind of work, though, is to have a dataset of which every image is part of the same ``macro-category'', like for example a dataset made of images of birds.
 Even though this is the ideal case,
@@
 
-			Another possibility to gather data, it's to ask people to list a certain number of objects or all the objects they can think about of the decided category.
+			\noindent Another possibility to gather data, it's to ask people to list a certain number of objects or all the objects the subjects can think about of the decided category.
 For example, let's assume the macro category decided
 			is ``birds''.
-It's possible to collect enough data by asking people to list a the first few examples of birds, using a predefined number.
+It's possible to collect enough data by asking people to list the first few examples of birds, using a predefined number.
 Moreover, it's possible to use a variant of this procedure and ask people
@@
 			method described in \ref{sec:typval}.
-% In case this type of data collection is used, the values of typicality should be also a question that asks the subjects to describe all the features that birds have in common
-			% with each other. This step will then be used for prototype construction.
+
+		\subsection{Test of the second data collection method}
+
+		\noindent To test the method of data collection described in \ref{sec:patv}, I collected the results of a small survey in which there were 10 questions, each asking to give the name of a bird.
+The number of
+		people that answered is not big enough to be a statistically relevant group, since the number of the answers is only $14$.
+
+		\begin{figure*}
+			\centerline{\includegraphics[width=\linewidth]{imgs/survey_hist.png}}
+			\caption{Results of the survey}
+			\label{fig:7}
+		\end{figure*}
+
+		\noindent In Figure \ref{fig:7} there are the results of the survey. Even though the number of answers was not very big, some problems still emerged.
+		\begin{itemize}
+
+			\item \textbf{Off-topic answers or blank answers}:
+
+				In this case, one of the answers had to be deleted from the answers, since the cited example was not part of the category decided for the survey.
+In particular, the survey asked for examples of birds,
+				while one of the answers was a mammal. This fact highlights a problem bound to the number of examples the user knows or can think of. In this example, the survey asked for $10$ names of birds,
+				which I thought was a reasonable number, but probably some of the subjects that took part to this survey could not think of a $10^{th}$ name, so just put a name of another animal. The solution 
+				to this problem is to apply some data cleaning to the answers to filter the examples that, eventually, are in the answers but not part of the given category.
+An analogue approach can be applied if the
+				subject leaves the answer blank for the same reason.
+
+			\item \textbf{Capitalization of examples}:
+
+				This problem is simpler than the previous one to solve, since it just involves the capitalization of the answers. If the survey starts accounting numerous results, it becomes difficult to 
+				compute the number of times that a particular example appears in the answers, so, most likely, there will be some automated scripts that compute all the needed statistics.
+This could be a problem since
+				in most of the programming languages, if not all, words like ``Robin'' and ``robin'' are considered different based on the capitalization. This problem is easily solvable by lowercasing all the 
+				answers.
+
+			\item \textbf{Typos of examples}:
+
+				This problem can be quite challenging to solve.
+In fact, subjects could make some mistakes when typing the answers, so for example a word like ``robin'' can become ``ribin'' or ``tobin'' for example.
+				Moreover, if more than one letter is wrong, some results like ``rivim'' instead of ``robin'' are possible, especially if the subjects compile the form via mobile devices. To solve this issue, 
+				it's possible to use some distance between strings, like for example the Levenshtein distance, which is used to find the distance between two strings. Although this could be a solution,
+				it's not guaranteed that the result is correct, so these results should always be checked again to prove they are correct and, most importantly, coherent with the category the survey is based on.
+
+			\item \textbf{Different specificity levels}:
+
+				This problem is very difficult to overcome. There is an example in the histogram reported as results. In the histogram, in fact, it's possible to note that there are both the ``eagle'' and 
+				the ``bald eagle'' labels. This means that different subjects can answer with different levels of specificity, since the ``eagle'' label is more general than its counterpart ``bald eagle''. 
+				This problem is presented also in an inter-species context, for example the ``Common kingfisher'' represents a single specie, representative of the ``kingfisher'' genus, while, for example, 
+				``Flamingo'' represents a family, of which some examples are the greater flamingo and the lesser flamingo, along with other species as well. 
+				Even though the problem is very clear, it's not very clear what to do in this case. A possibility is to decide that, in the case of the presented survey, 
+				the ``bald eagle'' label should be incorporated in the ``eagle'' 
+				label, making sure that all the instances of the most specific one are accounted as instances of the more general one. Another possibility is to keep both of the labels, so that the results of 
+				the survey are unaltered. Lastly, it's possible to assume that every label that identifies a group more general than a single specie, like a family or a whole order is referred to the most 
+				common specie of that family or order. The only way to know exactly which of these possibilities performs better is conducting some experiments and compare the obtained results.
+
+		\end{itemize}
+
+		\noindent Even with all these problems, the survey works quite well, since also with a few answers the results show that most of the subjects had mentioned the most common birds, like pigeons, while the
+		less common ones, like for examples peacocks, are mentioned fewer times.
+The results of this particular survey show that, a part for some examples, most of the birds appear only a few times.
+Although there
+		are some examples that are most likely outliers even with large numbers of subjects taking the survey, like ``Dodo'', some other examples, like ``Swift'' or ``Common blackbird'', 
+		are likely to be more typical with a larger number of people taking the survey.\\
+		The goal of the survey is to infer a measure of typicality based on how often a certain example appears in the results of the answers, and the result, at first glance, seems to be achieved.
+Although only
+		a test can prove this, it's very likely that with a larger group of subjects taking the survey, the results will differ more than with a small number of subjects.
 
@@
 
-			The two presented methods proposed for data collection are very different.
-Both of these have their own pros and cons.
+			\noindent The two presented methods proposed for data collection are very different.
+Both of these have their own peculiarities.
 The first method can help in having a typicality value for every image collected in the dataset,
 			while the second does not.
-The large number of images that should be used, though, it's not feasible to ask the subjects to rate the typicality value of all the images of the dataset.
+Given the large number of images that should be used, though, it's not feasible to ask the subjects to rate the typicality value of all the images of the dataset.
 In fact, it's very likely
@@
 			In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two
-			methods and decide which one is more convenient.
+			methods have the right weight and it's easier to decide which one is more convenient.
 			As alternative, it's possible to try both the methods and see which one gives better results.
@@
 		\noindent While collecting the needed data with the survey, it's possible to begin the feature extraction procedure.
-There are various possibilities for this step, as shown in the Section dedicated to feature extraction background.
+There are various possibilities for this step, as shown in Section \ref{sec:bfe}, which is
+		the section dedicated to feature extraction background. 
 		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient.
@@
 The first way is to use the data collected for
-		typicality judgments and collect also images of the birds that appear in the results. After collecting enough images, the feature extraction process can proceed as described earlier and use either  
+		typicality judgments and collect also images of the examples that appear in the results.
+After collecting enough images, the feature extraction process can proceed as described earlier and use either
 		classical or machine-learning-based feature extraction methods.
@@
 
-		\subsection{Classical feature extraction techniques}
+		\subsection{After classical feature extraction techniques\label{sec:cfet}}
 
@@
 For example, a prototype of a bird, could be
-			an imaginary bird with a shape that it's obtained with a weighted average of the shapes of all the birds in the image. For example, since a birds like sparrows and swallows are perceived as more 
-			typical than ostriches and penguins the prototype should resemble more swallows and sparrows than ostriches and penguins. To do so, the key factor is performing numerous analyses on various 
+			an imaginary bird with a shape that it's obtained with a weighted average of the shapes of all the birds in the image. For example, since birds like sparrows and swifts are perceived as more 
+			typical than ostriches and penguins the prototype should resemble more swifts and sparrows than ostriches and penguins. To do so, the key factor is performing numerous analyses on various 
 			different subjects, until there are enough data to have a statistical value.
@@
 				\end{subfigure}
-				\caption{Edge extraction of swallow and penguin}
-				\label{fig:7}
+				\caption{Edge extraction of swift and penguin}
+				\label{fig:8}
 			\end{figure*}
 
-		\noindent In Figure \ref{fig:7} there is an example of the edges of two different birds. Although both of the subjects of the original 
-		subjects are birds, one is much more typical than the other one.
-In this case, the prototype should try to match more the swallow edge than the penguin edge.
-A way to do so could make use deformable
+		\noindent In Figure \ref{fig:8} there is an example of the edges of two different birds. Although both of the original 
+		subjects are birds, one is much more typical than the other one. In this case, the prototype should try to match more the swift edge than the penguin edge. A way to do so could make use deformable 
 		template matching.
@@
 
-		\subsection{Machine learning feature extraction techniques}
+		\subsection{After machine learning feature extraction techniques\label{sec:mlfet}}
 
@@
 			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors.
-			%Allungare (?)
+The weights should be taken according to the perceived typicality
+			of the category example, which is the average of the measures collected with the survey.
 
-		\subsection{Other survey method}
+		\subsection{After the alternative data collection method}
 
-			%Diificile, da pensare bene.
+			\noindent If the method used for data collection is the one described in Section \ref{sec:patv}, the feature extraction can take two different paths. One of these two paths leads to collecting 
+			several images and applying one of the classical or machine learning-based feature extraction techniques.
+In this case, the prototype construction follows the guidelines given in Sections \ref{sec:cfet} and \ref{sec:mlfet}.
+			In case the features are not extracted directly from images, but from answers on the survey, the process is more complex. In particular, the construction should generate a prototype from 
+			scratch based on the indications on the survey. The importance of every feature can be deduced by how many subjects mention it in their description. The result should be in the form of an image. 
+			As mentioned when talking about the prototype construction after classical feature extraction methods, the image generated by this process should take into account more the features listed more 
+			times in the survey, since they would be features that more people identify as important.
+In a way similar to the one that is described earlier, the prototype must be built in the form of an image.
+			The challenge that this procedure presents, though, it's different than the one presented by the other method, since the image in this case has to be built from scratch, having only the indications of
+			those who participated to the survey.
+To make the prototype construction easier, there is the possibility to build from scratch a prototype for every answer of the survey and then merge them all in one
+			single image, taking into account the different contributions based on how frequently some characteristics are mentioned.
+In this way, even though the procedure demands the construction of more than one
+			image, the final prototype is obtained by summing all the single images using a weighted sum.
 
@@
 			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
-			a work by Carvalho written in 2019~\cite{electronics8080832}, %(\textbf{SOME CITATIONS}),
-			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the european union in the field of artificial intelligence.
+			a work by Carvalho written in 2019~\cite{electronics8080832}, 
+			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the European Union in the field of artificial intelligence.
 In particular, there is a document of
-			the act~\footnote{\url{https://eur-lex.europa.eu/resource.html?uri=cellar:e0649735-a372-11eb-9585-01aa75ed71a1.0001.02/DOC_1&format=PDF}} that states that there will be some requirements in terms of
-			transparency and intepretability for machine learning systems that are considered high-risk AI.
+			the act\footnote{\url{https://eur-lex.europa.eu/resource.html?uri=cellar:e0649735-a372-11eb-9585-01aa75ed71a1.0001.02/DOC_1&format=PDF}} that states that there will be some requirements in terms of
+			transparency and interpretability for machine learning systems that are considered high-risk AI.
 The growing interest produced some results, but still they're not enough to easily interpret machine learning
@@
 On the other side, algorithms
-			like the triangulation always have the same demand, that is lower than the demand of training a neural network, but surely higher than the demand of evaluating a single input on a neural network. 
-			Moreover, considering the possiblity to use transfer learning techniques, the training can become a fine-tuning or a domain adaptation, which means the computational load is lighter.
+			like the triangulation always have the same demand, that is lower than the demand of training a neural network, but surely higher than the demand of evaluating a single input on a convolutional neural network.
+			Moreover, considering the possibility to use transfer learning techniques, the training can become a fine-tuning or a domain adaptation problem, which means the computational load is lighter.
 Considering that
-			the fact that the training is a demanding task to be perfomed only once and that other algorithms may be less demanding but must be run multiple times, it's probably more convenient to train a neural
+			the fact that the training is a demanding task to be performed only once and that other algorithms may be less demanding but must be run multiple times, it's probably more convenient to train a neural
 			network.
@@
 			enough to perform a weighted average, a simpler operation if confronted with the construction of a new image that should take into account features of numerous other images.
+			Moreover, scientists will be presented a tough challenge, since the construction of an image using the average of other images is not an easy task.
+In this task there are in particular two problems.
+The first
+			one is that there is no clear algorithm to average two different images as it's requested in this paper, 
+			and it's even more difficult to compute a weighted average. In fact, the in Figure \ref{fig:8}, it's difficult to even imagine what the result of this weighted average should be.
+
+			\begin{figure*}[!t]
+				\centering
+				\begin{subfigure}[!t]{0.48\linewidth}
+					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
+				\end{subfigure}
+				\begin{subfigure}[!t]{0.48\linewidth}
+					\centerline{\includegraphics[height=0.4\textheight]{imgs/swallow_2_edges.jpg}}
+				\end{subfigure}
+				\caption{Edge extraction of different swifts}
+				\label{fig:9}
+			\end{figure*}
+
+			\noindent The second problem is concerning the weight of the image portrays the same example in different positions.
+Talking about birds, there is an example in Figure \ref{fig:9}.
+In this case, it's not clear
+			how much should the first image weigh compared to the second one, since they portray the same species of bird in different situations.
+As said before, there is no algorithm that can average the two images in the
+			way required by this paper, but in this case, most likely, the result would be a mix of two images that would not have much sense, since the swift is in different position, in one it's perched while in the other
+			image is flying. So, to work with this type of approach, an algorithm that computes the average of the two images should be implemented.\\
+			If the data are obtained witha the second data collection method proposed, the construction can take two different paths.
+For the first, which is collecting images based on the survey's answers, the
+			considerations done earlier remain valid, since in the end the feature extraction happens on an image dataset.
+There is another possibility, though, that is more difficult to implement.
+In this case, the
+			prototype is built from scratch, using the informations that the subjects gave in the survey.
+This method theoretically is more accurate than the others, since it can take into account only features
+			that the people answering have in mind.
+On the other hand, people could not list some features that they consider important because they take them for granted.
+An example is the presence of the beak in birds.
+			Most likely, the vast majority of people imagine a bird with a beak, but take for granted the presence of the beak, so it's unlikely that it's listed in the features.
+On the contrary, it's very likely that
+			most people will list, for example, wings in the features that a bird should have, without specifying which type of wings.
+
+			 \begin{figure*}
+				\centering
+				\begin{subfigure}{0.48\textwidth}
+					\centering
+					\includegraphics[width=\textwidth]{imgs/eagle_wing.jpg}
+					\caption{Eagle wing}    
+					\label{fig:9a}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}{0.48\textwidth}  
+					\centering 
+					\includegraphics[width=\textwidth]{imgs/seagull_wing.jpg}
+					\caption{Seagull wing}
+					%\label{fig:9b}
+				\end{subfigure}
+				\vskip\baselineskip
+				\begin{subfigure}{0.48\textwidth}   
+					\centering 
+					\includegraphics[width=\textwidth]{imgs/owl_wing.jpg}
+					\caption{Owl wing}
+					%\label{fig:9c}
+				\end{subfigure}
+				\hfill
+				\begin{subfigure}{0.48\textwidth}   
+					\centering 
+					\includegraphics[width=\textwidth]{imgs/pigeon_wing.png}
+					\caption{Pigeon wing}
+					%\label{fig:9d}
+				\end{subfigure}
+				\caption{Different types of wings of birds}
+				\label{fig:10}
+			\end{figure*}
+
+			\noindent In Figure \ref{fig:10} it's possible to see some wings of different birds.
+As shown by the images on the picture, the wings of different birds tend to be different, even if some have more
+			differences than others. For example, the eagle's wing and the owl's wing are more similar to each other than to the others, since both of them are raptors. Even though these two birds are part of 
+			the same order of birds, their wings differ from one another since the owl has a feather conformation that make sure that there is almost no sound when the bird is flying, while the eagle's wings 
+			help the bird fly with the minimum effort.
+The seagull and the pigeon wings, on the other hand, differ a lot from the wings of the two raptors, since they are part of another family, so they adapted
+			the shape of the wings for other goals. These considerations lead to understanding that even if a person, interviewed for the survey, tells that having wings it's a common characteristic of birds, 
+			it's important to understand what type of wings the subject is talking about. Moreover, the characteristics should be as precise as possible in terms of descriptive quality, since the prototype, a 
+			key factor of this work, relies on the description made by who is taking the survey.
+To be as precise as possible, the best way to proceed is to build the prototype with the subject that described it
+			or asking the subjects to draw a sketch of the prototype. To draw the prototypes with the subject present in that moment is something that it's not possible if the number of answers is large 
+			enough to be statistically relevant, while may be the case that asking people to draw a sketch and applying some post-processing to the image is easier than building all images from scratch and also
+			reduces the bias to which the data are exposed.
+In this case, the bias would originate from who builds the prototype, because this person can have its own idea of prototype of the given category and
+			interpret the indications in a certain way that does not reflect completely the original subject's idea.
 
@@
 
-		\subsection{Classic feature extraction techniques}
+		\subsection{Using classical feature extraction techniques\label{sec:slcfet}}
 
@@
 
-		\subsection{Machine learning feature extraction techniques}
+		\subsection{Using machine learning feature extraction techniques\label{sec:slmlfet}}
 
-			\noindent If the feature extraction process involved neural networks, after the prototype building step the result is not anymore an image but it's a vector of values.
+			\noindent If the feature extraction process involved neural networks, after the prototype building step the result is not any more an image but it's a vector of values.
 This implies that there is no need to
@@
 The rest of the procedure
-			is similar, since the siamese network will still be fed the features of the prototype and the features of an imaage of the dataset.
+			is similar, since the siamese network will still be fed the features of the prototype and the features of an image of the dataset.
 As in the previous case, the goal of this kind of prediction is to learn
 			a similarity metric using annotated values. After learning the metric, the network will be able to measure the similarity of the prototype and any other image. 
-			By doing so the couple of values \textit{perceived typicality - similarity measure} could reveal some interesting patterns.
+			As in the previous point, the couple of values \textit{perceived typicality - similarity measure} could reveal some interesting patterns.
+
+		\subsection{Using the alternative data collection method}
+
+			\noindent In case the data collection happened with the second method, the similarity learning happens with a siamese neural network which structure depends on the feature extraction method described.
+The
+			results, in fact, can be different.
+If the data collection is made by looking for images of the cited examples, the feature extraction process can follow two routes: the classical one and the machine learning
+			one.
+In both cases, the similarity learning follows the descriptions in \ref{sec:slcfet} and \ref{sec:slmlfet} respectively, since the resulting prototypes are images.
+In case the feature extraction did not happen through
+			the collection of images but creating an image following the features listed by the subjects of the survey, the similarity learning still happens with a siamese neural network, but with some differences.
+In fact
+			the image resulting from this process will have less features than an image retrieved online, because it's created from scratch using the indications of people that took the survey.
+Involving humans in
+			the feature extraction process, it's possible that the extracted features will not involve colour features, since the colour feature is dependant on the example of the class.
+If we consider the class ``bird'' as
+			example, the colour that people associate with birds is dependent on the species of the considered bird.
+If the example taken into consideration is the swift, the colour associated with this bird are, most likely,
+			black and white, while for example if the person thinks about a sparrow, the colour thought about are mostly some brown shades.
+In order to reduce as much as possible colour features, the images fed to
+			the siamese neural network should be preprocessed.
+Transforming the image to greyscale could be enough, but it should be better to perform a thresholding operation so that the colour features are reduced as much
+			as possible. In both cases, the required siamese network is a network that has two CNNs as embedding networks.
 
@@
 The type of measure that it's possible to use ranges a lot, from simple distances like the Manhattan distance
-			or the euclidean distance to more complex measures that can be defined by the user.
+			or the euclidean distance to more complex measures that can be defined by the user. An example of usual contrastive loss is 
+			\begin{center}
+				$-\log(\dfrac{e^{sim(z_i, z_j) / T)}}{\sum_{k=1, k\neq 1}^{2N} e^{sim(z_i, z_k) / T}})$
+			\end{center}
+			where $sim(z_i, z_k)$ is the vector similarity and $T$ is a temperature normalization factor.
+In this case, since the goal is to minimize the loss, the best scenario is the one that presents two similarity
+			vectors close to $1$, since this would result in $0$, which is the best value for a loss.
 
@@
 			decided to implement. For example, suppose that the vectors are $[2,\ 3]$ and $[5, 8]$. If the Manhattan distance is chosen as measure, the distance between the two defined vectors is $8$. 
-			Using the euclidean distance instead of the Manhattan distance, the result is $~5,83$.
+			Using the euclidean distance instead of the Manhattan distance, the result is $5,83 ca.$.
 In data science there are some possibilities for distance measurements, a part from euclidean and Manhattan distance.
@@
 			neural networks, the siamese network will only need fully connected layers, while it would need convolutional, pooling and fully connected layers if the features are extracted with in a classical way.
-			The only problem about the machine learning feature extraction techniques is, as mentioned in \ref{sec:cpc}, is the fact that we're still unable to interpret the features extracted by a CNN.
+			The only problem about the machine learning feature extraction techniques, as mentioned in \ref{sec:cpc}, is the fact that we're still unable to interpret the features extracted by a CNN.\\
+			Talking about the second data collection method, if the chosen method is to ask people to list the characteristics they think are most important, the result will probably involve less features.
+So, as an
+			educated guess, it's likely that the similarity learning will perform better in case the survey asks to rate the typicality on a scale.
+In fact, unless the features are too many and the model suffers of the
+			so-called curse of dimensionality, the more the features, the better the performance.
 
@@
 
-		\subsection{Possible relevant experiments}
+		\subsection{Possible relevant followings}
 
@@
 			of images.
-For example, if the first experiment is conducted on a dataset with bird images, it could be interesting to conduct the same experiment on a dataset that uses a different animal, like, for
+For example, if the first experiment is conducted on a dataset with bird images, it could be interesting to conduct the same experiment on a dataset that uses a different animal like, for
 			example, fishes.\\
@@
 Even though
-			it's not enough for a proof, could be an interesting starting point for neuroscientists to better understand how typicality works in human brain.\\
+			it's not enough for a proof, it could be an interesting starting point for neuroscientists to better understand how typicality works in human brain.\\
 			Another possibly interesting topic could be examining the results of the survey based on the region of the person answering.
@@
 			in North America, since the bald eagle is a national symbol, it's easier that people associate with it a higher typicality value. Moreover, there are a lot of different factors that can influence 
-			the typicality rates of images in people.
-For example, a farmer could be more inclined than people that live in a big city to think associate a chicken with the concept of ``bird'', and thus giving
+			the typicality rates of images in people. For example, a farmer could be more inclined than people that live in a big city to associate a chicken with the concept of ``bird'', and thus giving 
 			it a higher typicality.\\
-			Lastly, it's worth notice that in this paper the prototype is considered as the mean of the features extracted from all the the images of the dataset.
-A possibility that could be interesting would be
+			It's worth to notice that in this paper the prototype is considered as the mean of the features extracted from all the the images of the dataset. A possibility that could be interesting would be 
 			interesting to try to experiment the possibility to use different concept of prototype and implementing the correspondent methods of building it.\\
-			% Cognitive/learning disorders (?)
+			Lastly, there is another possibility in the medic field. In fact, if this experiment helps in understanding the way that knowledge is organized in the brain, it could be interesting to see if 
+			asking people with some knowledge-related or cognitive disorder the results of typicality are similar or not to the ones obtained by asking people without disorders. This experiment could give 
+			an insight about how knowledge is organized in brains of people with disorders, and if it's similar to the way brain of people without any disorder organize the knowledge.
 
-	\section{Conclusion}
+	\section{Overall considerations and conclusions}
 
-		The experiment proposed has the objective to help identifying, if it exists, a link between the typicality of a concept and the similarity to a prototype.
+		\noindent The experiment proposed has the objective to help identifying, if it exists, a link between the typicality of a concept and the similarity to a prototype.
 The work strongly relies on neural networks, in
@@
 		good statistics, the result can give an idea of the correlation between typicality and a prototype of a concept.
-
-	\appendix
-
-	\section{Appendix\label{sec:app}}
-
-		To test the method of data collection described in \ref{sec:patv}, I collected the results of a small survey in which there were 10 questions, each asking to give the name of a bird. The number of 
-		people that answered is not big enough to be a statistically relevant group, since the number of the answers is only $14$.
-
-		\begin{figure*}
-			\centerline{\includegraphics[width=\linewidth]{imgs/survey_hist.png}}
-			\caption{Results of the survey}
-			\label{fig:app}
-		\end{figure*}
-
-		\noindent In Figure \ref{fig:app} there are the results of the survey. Even though the number of answers was not very big, some problems were still emerged.
-		\begin{itemize}
-
-			\item \textbf{Off-topic answers or blank answers}:
-
-				\noindent In this case, one of the answers had to be deleted from the answers, since the cited example was not part of the category decided for the survey.
-In particular, the survey asked for examples of birds,
-				while one of the answers was ``gazelle''. This fact highlights a problem bound to the number of examples the user knows or can think of. In this example, the survey asked for $10$ names of birds,
-				which I thought was a reasonable number, but probably some of the subjects that took part to this survey could not think of a $10^{th}$ name, so just put a name of another animal. The solution 
-				to this problem is to apply some data cleaning to the answers to filter the examples that, eventually, are in the answers but not part of the given category.
-An analogue approach can be applied if the
-				subject leaves the answer blank for the same reason.
-
-			\item \textbf{Capitalization of examples}:
-
-				\noindent This problem is simpler than the previous one to solve, since it just involves the capitalization of the answers.
-If the survey starts accounting numerous results, it becomes difficult to
-				compute the number of times that a particular example appears in the answers, so, most likely, there will be some automated scripts that compute all the needed statistics.
-This could be a problem since
-				in most of the programming languages, if not all, words like ``Robin'' and ``robin'' are considered different based on the capitalization. This problem is easily solvable by lowercasing all the 
-				answers.
-
-			\item \textbf{Typos of examples}:
-
-				\noindent This problem can be quite challenging to solve.
-In fact, subjects could make some mistakes when typing the answers, so for example a word like ``robin'' can become ``ribin'' or ``tobin'' for example.
-				Moreover, if more than one letter is wrong, some results like ``rivim'' instead of ``robin'' are possible, especially if the subjects compile the form via mobile devices. To solve this issue, 
-				it's possible to use some distance between strings, like for example the Levenshtein distance, which is frequently used to find the distance between two strings. Although this could be a solution,
-				it's not guaranteed that the result is correct, so these results should always be checked again to prove they are correct and, most importantly, coherent with the category the survey is based on.
-
-			\item \textbf{Different specificity levels}:
-
-				\noindent This problem is very difficult to overcome.
-There is an example in the histogram reported as results.
-In the histogram, in fact, it's possible to note that there are both the ``eagle'' and
-				the ``bald eagle'' labels. This means that different subjects can answer with different levels of specificity, since the ``eagle'' label is more general than its counterpart ``bald eagle''. 
-				This problem is presented also in an inter-species context, for example the ``Common kingfisher'' represents a single specie, representative of the ``kingfisher'' genus, while, for example, 
-				``Flamingo'' represents a family, of which some examples are the greater flamingo and the lesser flamingo, along with other species as well. 
-				Even though the problem is very clear, it's not very clear what to do in this case. A possibility is to decide that, in this case, the ``bald eagle'' label should be incorporated in the ``eagle'' 
-				label, making sure that all the instances of the most specific one are accounted as instances of the more general one. Another possibility is to keep both of the labels, so that the results of 
-				the survey are unaltered. Lastly, it's possible to assume that every label that identifies a group more general than a single specie, like a family or a whole order is referred to the most 
-				common specie of that family or order. The only way to know exactly which of these possibilities performs better is conducting some experiments and compare the obtained results.
-
-		\end{itemize}
-
-		\noindent Even with all these problems, the survey works quite well, since also with a few answers the results show that most of the subjects had mentioned the most common birds, like pigeons, while the
-		less common ones, like for examples peacocks, are mentioned fewer times.
-The results of this particular survey show that, a part for some examples, most of the birds appear only a few times.
-Although there
-		are some examples that are most likely outliers even with large numbers of subjects taking the survey, like ``Dodo'', some other examples, like ``Swift'' or ``Common blackbird'', 
-		are likely to be more typical with a larger number of people taking the survey.\\
-		The goal of the survey is to infer a measure of typicality based on how often a certain example appears in the results of the answers, and the result, at first glance, seems to be achieved.
-Although only
-		a test can prove this, it's very likely that with a larger group of subjects taking the survey, the results will differ more than with a small number of subjects.
-
-	\newpage
+This experiment's proposition tells that the educated guess that lies behind this particular paper
+		is that there is a correlation, but if this educated guess is proven to be wrong would be an interesting result too.\\
+		The overall experiment is not conceptually complex, but some difficulties can be found in implementing some of the steps.
+The paper though, tries to give more than one alternative for each of the steps, so that there
+		is more than one possibility for the realization of the experiment itself.
+The scientists that would like to try to implement this experiment should decide which method they would like to implement, or if they
+		want to create a new method to use.\\
+		Concerning the data prototype construction methods, the biggest problem is that one of them requires a prototype construction from scratch.
+This operation is very time demanding, and even if the time could
+		be reduced by asking people to provide also a quick sketch of a prototype, it's not guaranteed that people will welcome that question and that they will actually draw something related to the prototype as they
+		perceive it.
+Moreover, when talking about the siamese neural network there is no way for humans to understand what the features that are extracted at the end of the embedding are, so this causes the requirement of
+		thresholding the dataset image, so that there are not features related to colours.
+If there was a way to map the features found by the CNN to humanly understandable features, there would be the possibility to
+		choose which features to use and which one to discard.
+Further understanding of the way that neural networks work and further knowledge about how to make the blackbox model humanly interpretable could give a great
+		advantage.
+Also, knowing this it could be possible to learn more about the difference in artificial neural networks compared to biological ones.
+Once there is enough understanding about this topic, it could be possible
+		to design artificial neural networks that are more similar to the human brain, but also differentiate them even more if there is the need of simulating a different way to process information. \\
 

### 2022-06-04 code_used_for_examples/edge_extraction.py

@@ -3,7 +3,7 @@ import os
 
 
 # Read the original image
-img = cv2.imread('imgs/obama.jpg')
+img = cv2.imread('imgs/rondine.jpeg')
 # Display original image
 cv2.imshow('Original', img)
 cv2.waitKey(0)
@@ -20,6 +20,6 @@ cv2.imshow('Canny Edge Detection', edges)
 cv2.waitKey(0)
 
 os.chdir('imgs')
-cv2.imwrite('obama_edges.jpg', edges)
+cv2.imwrite('swallow_2_edges.jpg', edges)
 
 cv2.destroyAllWindows()

### 2022-06-10 paper.tex
Removed all contracted forms for fomrality

@@
 
-		\noindent The typicality of a concept is a topic that needs a lot of exploration, since it's difficult to evaluate precisely the typicality of an object 
+		\noindent The typicality of a concept is a topic that needs a lot of exploration, since it is difficult to evaluate precisely the typicality of an object 
 		and also because the people's brains are always a little different from each other. The experiment I would like to propose, has the objective of 
@@
 		\noindent The possible applications of this experiment are widely ranged. First of all, this experiment could help neuroscientists understand how the knowledge is 
-		organized in the brain. By doing so, there is the possibility to increase the knowledge about the brain and how it works. Moreover, it's possible to confront 
+		organized in the brain. By doing so, there is the possibility to increase the knowledge about the brain and how it works. Moreover, it is possible to confront 
 		the way that a person with cognitive disorders or, more generally, some kind of mental disorder related to knowledge with the results of people without 
@@
 
-			\noindent Typicality is one of the key concepts that will be used in this paper, so it's fundamental that it's defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
+			\noindent Typicality is one of the key concepts that will be used in this paper, so it is fundamental that it is defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
 			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
@@
 					Some examples are the Sobel operator and the Canny edge detector. 
-					Each algorithm has its own peculiarities and it's the user's job to find 
+					Each algorithm has its own peculiarities and it is the user's job to find 
 					the most appropriate for its goal~\cite{owotogbe2019edge}.\\
@@
 						colour is one of the most important features humans can perceive. 
-						The features we can extract depend on the colour space, but once it's defined there are some possibilities. 
+						The features we can extract depend on the colour space, but once it is defined there are some possibilities. 
 						A few examples are colour histograms, colour moments and colour coherence vectors. 
@@
 Although this paper examines the techniques for
-					3D shapes, it's very likely that it can be adapted to extract 2D features from images.\\
+					3D shapes, it is very likely that it can be adapted to extract 2D features from images.\\
 					The background of this experiments is formed of some concepts that are not immediate. One of the concepts used as background is the minimum distortion correspondence. The other are, for example, 
@@
 					has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
-					In this paper's results it's reported that the best model architecture is DenseNet-169.
+					In this paper's results it is reported that the best model architecture is DenseNet-169.
 This kind of neural network, called Dense Nets, overcomes the problem of gradient vanishing.
@@
 The techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent
-					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it's probably more meaningful to use normal 
+					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it is probably more meaningful to use normal 
 					images than these ones.
@@
 						\item \textbf{Dense layer}:\\
-							The dense layer is not peculiar of CNNs, in fact it's found in almost all types of neural networks. It consists of a set of neurons that are connected with every neuron of the previous 
+							The dense layer is not peculiar of CNNs, in fact it is found in almost all types of neural networks. It consists of a set of neurons that are connected with every neuron of the previous 
 							layer. Dense layers are usually used towards the end of the network.
@@
 For example, ImageNet, which is one of the most famous image datasets, contains more than 1 million images that are divided
-			into 1000 classes. Generally, it's possible to use these datasets, which have different macro categories by filtering the input images based on the macro category the experiment is based on.
+			into 1000 classes. Generally, it is possible to use these datasets, which have different macro categories by filtering the input images based on the macro category the experiment is based on.
 
@@
 			image at a time to the subject that is taking the survey and asks to rate the typicality of the object portrayed in the image, possibly in a given range.
-If that's the case, a range between $1$ and $10$
+If that is the case, a range between $1$ and $10$
 			could be the best decision since people are quite used to rate in this range. Once there are enough results, the various rates should be averaged so that there is a single measure that takes into 
@@
 
-			\noindent Another possibility to gather data, it's to ask people to list a certain number of objects or all the objects the subjects can think about of the decided category.
-For example, let's assume the macro category decided
+			\noindent Another possibility to gather data, it is to ask people to list a certain number of objects or all the objects the subjects can think about of the decided category.
+For example, let us assume the macro category decided
 			is ``birds''.
-It's possible to collect enough data by asking people to list the first few examples of birds, using a predefined number.
-Moreover, it's possible to use a variant of this procedure and ask people
+It is possible to collect enough data by asking people to list the first few examples of birds, using a predefined number.
+Moreover, it is possible to use a variant of this procedure and ask people
 			to list all the examples of birds that they can think of.
@@
 				Moreover, if more than one letter is wrong, some results like ``rivim'' instead of ``robin'' are possible, especially if the subjects compile the form via mobile devices. To solve this issue, 
-				it's possible to use some distance between strings, like for example the Levenshtein distance, which is used to find the distance between two strings. Although this could be a solution,
-				it's not guaranteed that the result is correct, so these results should always be checked again to prove they are correct and, most importantly, coherent with the category the survey is based on.
+				it is possible to use some distance between strings, like for example the Levenshtein distance, which is used to find the distance between two strings. Although this could be a solution,
+				it is not guaranteed that the result is correct, so these results should always be checked again to prove they are correct and, most importantly, coherent with the category the survey is based on.
 
@@
 
-				This problem is very difficult to overcome. There is an example in the histogram reported as results. In the histogram, in fact, it's possible to note that there are both the ``eagle'' and 
+				This problem is very difficult to overcome. There is an example in the histogram reported as results. In the histogram, in fact, it is possible to note that there are both the ``eagle'' and 
 				the ``bald eagle'' labels. This means that different subjects can answer with different levels of specificity, since the ``eagle'' label is more general than its counterpart ``bald eagle''. 
@@
 				``Flamingo'' represents a family, of which some examples are the greater flamingo and the lesser flamingo, along with other species as well. 
-				Even though the problem is very clear, it's not very clear what to do in this case. A possibility is to decide that, in the case of the presented survey, 
+				Even though the problem is very clear, it is not very clear what to do in this case. A possibility is to decide that, in the case of the presented survey, 
 				the ``bald eagle'' label should be incorporated in the ``eagle'' 
 				label, making sure that all the instances of the most specific one are accounted as instances of the more general one. Another possibility is to keep both of the labels, so that the results of 
-				the survey are unaltered. Lastly, it's possible to assume that every label that identifies a group more general than a single specie, like a family or a whole order is referred to the most 
+				the survey are unaltered. Lastly, it is possible to assume that every label that identifies a group more general than a single specie, like a family or a whole order is referred to the most 
 				common specie of that family or order. The only way to know exactly which of these possibilities performs better is conducting some experiments and compare the obtained results.
@@
 Although only
-		a test can prove this, it's very likely that with a larger group of subjects taking the survey, the results will differ more than with a small number of subjects.
+		a test can prove this, it is very likely that with a larger group of subjects taking the survey, the results will differ more than with a small number of subjects.
 
@@
 			while the second does not.
-Given the large number of images that should be used, though, it's not feasible to ask the subjects to rate the typicality value of all the images of the dataset.
-In fact, it's very likely
+Given the large number of images that should be used, though, it is not feasible to ask the subjects to rate the typicality value of all the images of the dataset.
+In fact, it is very likely
 			that a subject that has to rate the typicality of a large number of images will be tired after a certain number of images, polluting the results of the survey.
@@
 Another
-			problem with this method it's that it has a possible bias.
+			problem with this method it is that it has a possible bias.
 In fact, if a person sees a bird, for example a swan, or a duck, and is asked to rate its typicality, most likely will rate it in the higher part
-			of the scale, while if asked to list a certain number of birds it's more likely that it's not present than that it's present.\\
-			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject didn't think of.
-			Recalling the previous example with the swan, if a person does not think of the swan, it won't be present in the list created by the subject.
+			of the scale, while if asked to list a certain number of birds it is more likely that it is not present than that it is present.\\
+			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject did not think of.
+			Recalling the previous example with the swan, if a person does not think of the swan, it would not be present in the list created by the subject.
 This could result in a lower bias, but it comes at the cost
@@
 			In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two
-			methods have the right weight and it's easier to decide which one is more convenient.
-			As alternative, it's possible to try both the methods and see which one gives better results.
+			methods have the right weight and it is easier to decide which one is more convenient.
+			As alternative, it is possible to try both the methods and see which one gives better results.
 In this way, both the possibilities will be used and there is the possibility to see which one is better in
@@
 
-		\noindent While collecting the needed data with the survey, it's possible to begin the feature extraction procedure.
+		\noindent While collecting the needed data with the survey, it is possible to begin the feature extraction procedure.
 There are various possibilities for this step, as shown in Section \ref{sec:bfe}, which is
@@
 		human have listed, so only the features that are considered important by humans themselves.
-Although it's theoretically possible, this procedure will result in numerous complication in prototype construction.
+Although it is theoretically possible, this procedure will result in numerous complication in prototype construction.
 
@@
 For example, a prototype of a bird, could be
-			an imaginary bird with a shape that it's obtained with a weighted average of the shapes of all the birds in the image. For example, since birds like sparrows and swifts are perceived as more 
+			an imaginary bird with a shape that it is obtained with a weighted average of the shapes of all the birds in the image. For example, since birds like sparrows and swifts are perceived as more 
 			typical than ostriches and penguins the prototype should resemble more swifts and sparrows than ostriches and penguins. To do so, the key factor is performing numerous analyses on various 
@@
 
-			\noindent In case machine learning feature extraction techniques were used, it's conceptually and practically easier to compute the average features.
+			\noindent In case machine learning feature extraction techniques were used, it is conceptually and practically easier to compute the average features.
 In fact, the features extracted by machine learning techniques are
-			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors.
+			in the form of arrays of numbers, so to compute the prototype of the image in this form it is enough to take the weighted average of the vectors.
 The weights should be taken according to the perceived typicality
@@
 In a way similar to the one that is described earlier, the prototype must be built in the form of an image.
-			The challenge that this procedure presents, though, it's different than the one presented by the other method, since the image in this case has to be built from scratch, having only the indications of
+			The challenge that this procedure presents, though, it is different than the one presented by the other method, since the image in this case has to be built from scratch, having only the indications of
 			those who participated to the survey.
@@
 			transparency and interpretability for machine learning systems that are considered high-risk AI.
-The growing interest produced some results, but still they're not enough to easily interpret machine learning
+The growing interest produced some results, but still they are not enough to easily interpret machine learning
 			features.\\
@@
 			used, the human interpretability will be possible, and with that in mind it would be probably more convenient to extract the features using neural networks. The reason behind this consideration is 
-			that although the training of a neural network can be expensive in computational terms, the evaluation of an input on a trained network it's not very computationally demanding.
+			that although the training of a neural network can be expensive in computational terms, the evaluation of an input on a trained network it is not very computationally demanding.
 On the other side, algorithms
@@
 Considering that
-			the fact that the training is a demanding task to be performed only once and that other algorithms may be less demanding but must be run multiple times, it's probably more convenient to train a neural
+			the fact that the training is a demanding task to be performed only once and that other algorithms may be less demanding but must be run multiple times, it is probably more convenient to train a neural
 			network.
-Moreover, not only the feature extraction process is convenient, but also the prototype construction itself is more convenient if the features are in the form of numerical parameters, since it's
+Moreover, not only the feature extraction process is convenient, but also the prototype construction itself is more convenient if the features are in the form of numerical parameters, since it is
 			enough to perform a weighted average, a simpler operation if confronted with the construction of a new image that should take into account features of numerous other images.
@@
 The first
-			one is that there is no clear algorithm to average two different images as it's requested in this paper, 
-			and it's even more difficult to compute a weighted average. In fact, the in Figure \ref{fig:8}, it's difficult to even imagine what the result of this weighted average should be.
+			one is that there is no clear algorithm to average two different images as it is requested in this paper, 
+			and it is even more difficult to compute a weighted average. In fact, the in Figure \ref{fig:8}, it is difficult to even imagine what the result of this weighted average should be.
 
@@
 Talking about birds, there is an example in Figure \ref{fig:9}.
-In this case, it's not clear
+In this case, it is not clear
 			how much should the first image weigh compared to the second one, since they portray the same species of bird in different situations.
 As said before, there is no algorithm that can average the two images in the
-			way required by this paper, but in this case, most likely, the result would be a mix of two images that would not have much sense, since the swift is in different position, in one it's perched while in the other
+			way required by this paper, but in this case, most likely, the result would be a mix of two images that would not have much sense, since the swift is in different position, in one it is perched while in the other
 			image is flying. So, to work with this type of approach, an algorithm that computes the average of the two images should be implemented.\\
@@
 An example is the presence of the beak in birds.
-			Most likely, the vast majority of people imagine a bird with a beak, but take for granted the presence of the beak, so it's unlikely that it's listed in the features.
-On the contrary, it's very likely that
+			Most likely, the vast majority of people imagine a bird with a beak, but take for granted the presence of the beak, so it is unlikely that it is listed in the features.
+On the contrary, it is very likely that
 			most people will list, for example, wings in the features that a bird should have, without specifying which type of wings.
@@
 
-			\noindent In Figure \ref{fig:10} it's possible to see some wings of different birds.
+			\noindent In Figure \ref{fig:10} it is possible to see some wings of different birds.
 As shown by the images on the picture, the wings of different birds tend to be different, even if some have more
@@
 The seagull and the pigeon wings, on the other hand, differ a lot from the wings of the two raptors, since they are part of another family, so they adapted
-			the shape of the wings for other goals. These considerations lead to understanding that even if a person, interviewed for the survey, tells that having wings it's a common characteristic of birds, 
-			it's important to understand what type of wings the subject is talking about. Moreover, the characteristics should be as precise as possible in terms of descriptive quality, since the prototype, a 
+			the shape of the wings for other goals.
+These considerations lead to understanding that even if a person, interviewed for the survey, tells that having wings it is a common characteristic of birds,
+			it is important to understand what type of wings the subject is talking about.
+Moreover, the characteristics should be as precise as possible in terms of descriptive quality, since the prototype, a
 			key factor of this work, relies on the description made by who is taking the survey.
 To be as precise as possible, the best way to proceed is to build the prototype with the subject that described it
-			or asking the subjects to draw a sketch of the prototype. To draw the prototypes with the subject present in that moment is something that it's not possible if the number of answers is large 
+			or asking the subjects to draw a sketch of the prototype. To draw the prototypes with the subject present in that moment is something that it is not possible if the number of answers is large 
 			enough to be statistically relevant, while may be the case that asking people to draw a sketch and applying some post-processing to the image is easier than building all images from scratch and also
@@
 
-			\noindent If the feature extraction process involved neural networks, after the prototype building step the result is not any more an image but it's a vector of values.
+			\noindent If the feature extraction process involved neural networks, after the prototype building step the result is not any more an image but it is a vector of values.
 This implies that there is no need to
-			use a convolutional neural network as embedding, but it's enough to have some fully connected layers that will be merged in a single fully connected network for the similarity learning.
+			use a convolutional neural network as embedding, but it is enough to have some fully connected layers that will be merged in a single fully connected network for the similarity learning.
 The rest of the procedure
@@
 In fact
-			the image resulting from this process will have less features than an image retrieved online, because it's created from scratch using the indications of people that took the survey.
+			the image resulting from this process will have less features than an image retrieved online, because it is created from scratch using the indications of people that took the survey.
 Involving humans in
-			the feature extraction process, it's possible that the extracted features will not involve colour features, since the colour feature is dependant on the example of the class.
+			the feature extraction process, it is possible that the extracted features will not involve colour features, since the colour feature is dependant on the example of the class.
 If we consider the class ``bird'' as
@@
 			of loss is based on a distance measure that should be defined by who is conducting the experiment.
-The type of measure that it's possible to use ranges a lot, from simple distances like the Manhattan distance
+The type of measure that it is possible to use ranges a lot, from simple distances like the Manhattan distance
 			or the euclidean distance to more complex measures that can be defined by the user. An example of usual contrastive loss is 
@@
 			neural networks, the siamese network will only need fully connected layers, while it would need convolutional, pooling and fully connected layers if the features are extracted with in a classical way.
-			The only problem about the machine learning feature extraction techniques, as mentioned in \ref{sec:cpc}, is the fact that we're still unable to interpret the features extracted by a CNN.\\
+			The only problem about the machine learning feature extraction techniques, as mentioned in \ref{sec:cpc}, is the fact that we are still unable to interpret the features extracted by a CNN.\\
 			Talking about the second data collection method, if the chosen method is to ask people to list the characteristics they think are most important, the result will probably involve less features.
 So, as an
-			educated guess, it's likely that the similarity learning will perform better in case the survey asks to rate the typicality on a scale.
+			educated guess, it is likely that the similarity learning will perform better in case the survey asks to rate the typicality on a scale.
 In fact, unless the features are too many and the model suffers of the
@@
 			Another possibility is to adopt a variant of the previously described network.
-For example, it's possible to use a variant of siamese neural networks that uses triplets for training.
+For example, it is possible to use a variant of siamese neural networks that uses triplets for training.
 In this version,
@@
 Even though one of the two methods is not
-			interpretable by humans, it's still interesting trying to understand which of the methods is more efficient in detecting features relevant for the similarity learning. Moreover, if the results 
+			interpretable by humans, it is still interesting trying to understand which of the methods is more efficient in detecting features relevant for the similarity learning. Moreover, if the results 
 			indicate that the machine learning techniques are more efficient, could be a push in the research that try to understand the neural networks' feature extraction method. This could be interesting 
@@
 Even though
-			it's not enough for a proof, it could be an interesting starting point for neuroscientists to better understand how typicality works in human brain.\\
+			it is not enough for a proof, it could be an interesting starting point for neuroscientists to better understand how typicality works in human brain.\\
 			Another possibly interesting topic could be examining the results of the survey based on the region of the person answering.
-In fact, it's possible that different regions, that have slightly different
+In fact, it is possible that different regions, that have slightly different
 			cultures and that may result in slightly different typicality perception.
-For example, in Europe the eagles are not common, so it's very likely that people will give a high typicality to eagles, while
-			in North America, since the bald eagle is a national symbol, it's easier that people associate with it a higher typicality value. Moreover, there are a lot of different factors that can influence 
+For example, in Europe the eagles are not common, so it is very likely that people will give a high typicality to eagles, while
+			in North America, since the bald eagle is a national symbol, it is easier that people associate with it a higher typicality value. Moreover, there are a lot of different factors that can influence 
 			the typicality rates of images in people. For example, a farmer could be more inclined than people that live in a big city to associate a chicken with the concept of ``bird'', and thus giving 
 			it a higher typicality.\\
-			It's worth to notice that in this paper the prototype is considered as the mean of the features extracted from all the the images of the dataset. A possibility that could be interesting would be 
+			It is worth to notice that in this paper the prototype is considered as the mean of the features extracted from all the the images of the dataset. A possibility that could be interesting would be 
 			interesting to try to experiment the possibility to use different concept of prototype and implementing the correspondent methods of building it.\\
@@
 			asking people with some knowledge-related or cognitive disorder the results of typicality are similar or not to the ones obtained by asking people without disorders. This experiment could give 
-			an insight about how knowledge is organized in brains of people with disorders, and if it's similar to the way brain of people without any disorder organize the knowledge.
+			an insight about how knowledge is organized in brains of people with disorders, and if it is similar to the way brain of people without any disorder organize the knowledge.
 
@@
 This operation is very time demanding, and even if the time could
-		be reduced by asking people to provide also a quick sketch of a prototype, it's not guaranteed that people will welcome that question and that they will actually draw something related to the prototype as they
+		be reduced by asking people to provide also a quick sketch of a prototype, it is not guaranteed that people will welcome that question and that they will actually draw something related to the prototype as they
 		perceive it.

### 2022-06-19 paper.tex
Added prototype section in background

@@
 
+		\subsection{Prototypes}
+
+			\noindent Prototypes are another key concept used in this paper and, as the concept of typicality, should be defined. In this case, there are some differences based on the field that it is 
+			examined. According to Murphy's Big Book of Concepts\cite{Murphy:2002}, a prototype is the best example of a category, which corresponds to the most typical item. In this case 
+			it is specified that this item may not be something that exists physically, but it is an average of what people see from real world examples. Adopting the example that the 
+			author uses in the book, which is about dogs, ``just your abstraction of what dogs are most often like''. This opens the possibility to the fact that every person has, for the 
+			same category, a different prototype. That is why, in this paper, the prototypes will be treated as an average, among different people, of the examples weighted with the 
+			average perceived typicality.\\
+			Although this is the concept of prototype that will be used in this paper, there are numerous different possibilities. For example, could be intended in a software-engineering way 
+			as the first example of a new product, or in a HCI-like way as a representation of conceptual design as stated by Prof. Narges Mahyar of the University of 
+			Massachusetts \cite{hciprot}. Another example is the concept of prototype used by Smith et al. in an article, in which they stated that a prototype is ``a prestored representation 
+			of the usual properties associated with the concept's instances'' \cite{smith1988combining}. This view in some way generalizes the definition expressed by Murphy in his book. \\
+			For the goal of this paper, the best way to define a prototype is the one used by Murphy, although with a small modification to take into account also the typicality of every 
+			example to create the prototype. Also Smith's way to define a prototype would be interesting to use, but since Murphy's way is a bit more specific, it is probably easier to use.
+
 		\subsection{Feature extraction\label{sec:bfe}}
@@
 					there are some examples of techniques used to extract features. 
-					In the first one, the authors present different types of features and then some techniques to extract them. 
-					These are:
+					In this paper, the authors present different types of features and then some techniques to extract them. 
+					Some of the most important are:
 
@@
 
-						\item \textbf{Chain Code Histogram of Character Contour}:
-
-							This method is based on a contour following technique. 
-							The contour following uses a chain coding standard proposed by Freeman, that assigns a value to every pixel to identify the next pixel in the border.
-
-						\item \textbf{Finding Intersection/Junction in character}:
-
-							Using the same standard proposed by Freeman used in Chain Code Histogram, there is the possibility to count intersections (or junctions) and open ends in a figure.
-
-						\item \textbf{Transition feature}:
-
-							This method is based on the transition from background to foreground. 
-							There are different techniques that can work both on gray level images or in 4-connected or 8-connected images.
-
 					\end{itemize}
@@
 				were excluded from the list. These excluded techniques can still be used, but may have worse results or may require some adaptation. 
-				The techniques were: Fractal theory techniques, Shadow features of character, Sector approach for feature extraction, 
+				The techniques were: Fractal theory techniques, Chain Code Histogram of Character Contour, Finding Intersection/Junction in character, 
+				Shadow features of character, Sector approach for feature extraction, Transition feature
 				Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.\\
@@
 
-					\item \textbf{colour features}:
+					\item \textbf{Colour features}:
 
-						colour is one of the most important features humans can perceive. 
+						Colour is one of the most important features humans can perceive. 
 						The features we can extract depend on the colour space, but once it is defined there are some possibilities. 
@@
 					\centerline{\includegraphics[width=\linewidth]{imgs/obama_histogram.png}}
-					\caption{Color histogram of the image used in \ref{fig:1}}
+					\caption{Color histogram of the image used in Figure \ref{fig:1}}
 					\label{fig:2}
@@
 					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually require an initialization near to the correct solution, 
-					although this is not required for the algorithm presented in this paper. 
-					For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor.
-In fact, using the order of perfect elimination (property of the every triangulated
-					simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
-					update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
-					The learning of the parameters can be seen as looking for the location with the highest.
-The matching problem is then fed to a statistical framework that computes the configuration minimizing the
-					energy cost, which corresponds to the best template match.
+					although this is not required for the algorithm presented in this paper. For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor.
 
@@
 					After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
-					In 2019, Halimi et al.
-wrote a paper about a feature extraction technique that they implemented using unsupervised deep learning~\cite{halimi2019unsupervised}.
-Although this paper examines the techniques for
-					3D shapes, it is very likely that it can be adapted to extract 2D features from images.\\
-					The background of this experiments is formed of some concepts that are not immediate. One of the concepts used as background is the minimum distortion correspondence. The other are, for example, 
-					descriptor learning, functional maps and deep functional maps. These concepts serve as a base for all the work done later. \\
-					In particular, the authors focus on unsupervised deep functional maps. The authors state that the main contribution of their paper is that they introduce a technique with which they can 
-					avoid annotating a lot of data before training a model. After reducing the number of vertices to a number between 5000 and 7000, the authors used a deep functional map network. The inputs are 
-					fed to two residual neural networks, which compute a dense descriptor fields.
-These descriptors, are the inputs to the functional map layer.
-Lastly, as post processing, a point-wise map recovery was
-					applied and, after that, the shape was upscaled to the original resolution.
-
-					\noindent In 2019, there is another paper, written by Varshni et al.
-that proposes another method~\cite{varshni2019pneumonia}.
-This paper has the objective to classify images using CNNs to understand if a patient
-					has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
+					\noindent In 2019, a paper written by Varshni et al. that proposes a method~\cite{varshni2019pneumonia} to classify images using CNNs, trying to understand if a patient 
+					has pneumonia or not. After the preprocessing, there is the feature extraction process. For this step, the authors used different pretrained models.
 					In this paper's results it is reported that the best model architecture is DenseNet-169.
-This kind of neural network, called Dense Nets, overcomes the problem of gradient vanishing.
-The model used in
-					particular for the work of this paper had 4 dense blocks and 3 transition layers. Then there is a classification layer.
 

### 2022-06-22 paper.tex
Added typicality ranking system

@@
 For example, ImageNet, which is one of the most famous image datasets, contains more than 1 million images that are divided
-			into 1000 classes. Generally, it is possible to use these datasets, which have different macro categories by filtering the input images based on the macro category the experiment is based on.
+			into 1000 classes. Generally, it is possible to use these datasets, which have different macro categories, by filtering the input images based on the macro category the experiment uses.
 
-		\subsection{Typicality values\label{sec:typval}}
+		\subsection{Rating based method for typicality values\label{sec:typval}}
 
@@
 			account every rate taken from the survey. The number of people that should participate in the experiment should be high enough to be a meaningful statistical group.
+
+		\subsection{Typicality ranking methods for typicality values}
+
+			\noindent Another possibility for collecting typicality values is the typicality ranking.
+With this method the researcher asks subjects to rank a set of objects based on their typicality.
+After doing so
+			and collecting the data, the researcher should infer the typicality values based on the ranking.
+The ranking, as the rating described in \ref{sec:typval}, cannot be performed on all images of the dataset,
+			so it's necessary to split the ranking and rank the images in different forms and then use the informations coming from different subjects and infer the informations about typicality from these answers.
 
@@
 
-		\subsection{Test of the second data collection method}
+		\subsection{Test of the alternative data collection method}
 
@@
 The first method can help in having a typicality value for every image collected in the dataset,
-			while the second does not.
+			while the alternative does not.
 Given the large number of images that should be used, though, it is not feasible to ask the subjects to rate the typicality value of all the images of the dataset.
@@
 			image is flying. So, to work with this type of approach, an algorithm that computes the average of the two images should be implemented.\\
-			If the data are obtained witha the second data collection method proposed, the construction can take two different paths.
+			If the data are obtained with the alternative data collection method proposed, the construction can take two different paths.
 For the first, which is collecting images based on the survey's answers, the
@@
 
-			\noindent In case the data collection happened with the second method, the similarity learning happens with a siamese neural network which structure depends on the feature extraction method described.
+			\noindent In case the data collection happened with the alternative method, the similarity learning happens with a siamese neural network which structure depends on the feature extraction method described.
 The
@@
 			The only problem about the machine learning feature extraction techniques, as mentioned in \ref{sec:cpc}, is the fact that we are still unable to interpret the features extracted by a CNN.\\
-			Talking about the second data collection method, if the chosen method is to ask people to list the characteristics they think are most important, the result will probably involve less features.
+			Talking about the alternative data collection method, if the chosen method is to ask people to list the characteristics they think are most important, the result will probably involve less features.
 So, as an
@@
 			It is worth to notice that in this paper the prototype is considered as the mean of the features extracted from all the the images of the dataset. A possibility that could be interesting would be 
-			interesting to try to experiment the possibility to use different concept of prototype and implementing the correspondent methods of building it.\\
+			to try to experiment the possibility to use different concept of prototype and implementing the correspondent methods of building it, possibly even with Smith's concept of prototype.\\
 			Lastly, there is another possibility in the medic field. In fact, if this experiment helps in understanding the way that knowledge is organized in the brain, it could be interesting to see if 

### 2022-06-23 paper.tex
Fixed data collection methods

@@
 
-		\subsection{Considerations about the survey}
+		\subsection{Considerations about the survey\lable{sec:cas}}
 
-			\noindent The two presented methods proposed for data collection are very different.
-Both of these have their own peculiarities.
-The first method can help in having a typicality value for every image collected in the dataset,
-			while the alternative does not.
-Given the large number of images that should be used, though, it is not feasible to ask the subjects to rate the typicality value of all the images of the dataset.
-In fact, it is very likely
-			that a subject that has to rate the typicality of a large number of images will be tired after a certain number of images, polluting the results of the survey.
-A possible solution to this problem is to
-			divide the survey so that subjects have to rate the typicality of a limited number of images.
-This method would result in a lower amount of data, but at the same time, a more precise amount of data.
-Another
-			problem with this method it is that it has a possible bias.
-In fact, if a person sees a bird, for example a swan, or a duck, and is asked to rate its typicality, most likely will rate it in the higher part
-			of the scale, while if asked to list a certain number of birds it is more likely that it is not present than that it is present.\\
-			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject did not think of.
-			Recalling the previous example with the swan, if a person does not think of the swan, it would not be present in the list created by the subject.
-This could result in a lower bias, but it comes at the cost
-			of having to interview more people and, most likely, not having enough data for some of the examples.
-In this approach, the more a bird is typical, the more it appears in the lists and in higher positions.
-			There is an example in the appendix.
-Even though this method has the advantage of having less bias, has a  great drawback.
-That is, in particular, the fact that the prototype construction is very difficult.\\
+			\subsubsection{Considerations}
+				\noindent The first two presented methods have a quite similar concept behind them.
+Although it is still a matter of discussion which one is more reliable, especially in children, as seen in \cite{maridaki1997rating}
+				and \cite{10.1371/journal.pone.0157936}, both these methods have been used to collect typicality informations. The main difference in these two methods is that the first one, which is based on 
+				ratings, the researchers may have biased data since it is possible that seeing a picture of an example of the category the subject can be biased.
+On the other hand, the other method does not present
+				this kind of bias, but presents a higher difficulty on in extracting the typicality values. \\
+				The alternative possible proposed method, can show a lower bias than the bias of the rating method since no images influence the subject's ratings.
+Moreover, it is easier to infer a typicality value
+				than in the ranking method, since a higher position on the list corresponds to a higher typicality. 
+				Another positive aspect of this method is that if a person did not think of a particular example, it won't appear on the ratings. This fact can help identifying the real typicality 
+				without the possible bias introduced by presenting to a subject an image of an example that did not come to mind.
+
+			\subsubsection{Limitations and negative aspects}
+
+				The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole 
+				dataset, since it must have many images.
+In fact, it is very likely that a subject that has to rate or rank many examples will be tired after a certain number of images, polluting the results of the survey.
+				The possible solution to this problem, is to give the subjects a subset of images to rate or rank.
+In this way, the collected data are most likely more reliable than the ones collected on all the dataset,
+				so it is more accurate the final result. \\
+				Regarding only the typicality rating system, there is another problem. As hinted in previously, there is the possibility that this procedure leads to biased data. That is true because the form 
+				created to collect the data, presents an example of an object that the subjects may not have thought of, and presenting the image, it may be possible that the subject gives a biased answer since 
+				the image could have influenced the subject's judgement. For example, let us assume that the category chosen for the experiments is ``bird''. If a person is presented and image of a swan, 
+				or a duck, and is asked to rate its typicality, most likely will rate it in the higher part of the scale, while if asked to list a certain number of birds it is more likely that it is not 
+				present than that it is present.\\
+				Talking about the ranking system, also this method can present biased data, since also this method presents the images, even if the bias is probably lower than the one that could result with the ranking system.
+				The major problem, with this method, is that the researcher must also design an algorithm to infer the typicality values from the rankings.
+This is a very difficult algorithm to design, since the rankings must
+				find a mapping to a scale.\\
+				The alternative possibility described, can result in a lower bias since no images influence the subject's judgments. Recalling the previous example, in fact, if the subject did not think of 
+				ducks and swans in the category ``bird'', these examples will not appear on the list. Although this technique presents a lower bias, it results in a great difficulty in prototype construction.
+
+			\subsubsection{Considerations on how to choose}
 				In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two

### 2022-06-23 paper.tex
Added limitation on FE

@@
 
-				The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole 
+				\noindent The biggest problematic related to the first two methods presented, which are the rating and the ranking systems, is that it is not feasible to either rate or rank every example in the whole
 				dataset, since it must have many images.
@@
 			\subsubsection{Considerations on how to choose}
-				In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two
+
+				\noindent In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two
 				methods have the right weight and it is easier to decide which one is more convenient.
@@
 Since feature extraction has already been described in the paper, this section will
-		present a discussion about the results of the presented methods' results. The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
+		present a discussion about the results of the presented methods' results.
+
+		\subsection{Considerations on feature extraction}
+
+			\noindent The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
 			In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process.
@@
 			edge extracted is correct or not seeing the original image.
-For example, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left,
+In fact, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left,
 			while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
@@
 After collecting enough images, the feature extraction process can proceed as described earlier and use either
-		classical or machine-learning-based feature extraction methods.
+			classical or machine learning based feature extraction methods.
 Although this is a possibility, there could be an alternative.
@@
 Although it is theoretically possible, this procedure will result in numerous complication in prototype construction.
+
+		\subsection{Limitations of feature extraction}
+
+			\noindent Examining the proposed methodologies, there are some limitations that can be seen.\\
+			Talking about classical feature extraction techniques, for example, the first question that comes to mind is if these processes lose a lot of informations.
+For example, the edge detection algorithm loses all
+			the informations about the colours.
+Since numerous methods exists and are finalized in extracting various informations from an image, there is the possibility to preprocess through different steps the
+			images and collect the highest number possible of informations and combine them when constructing the prototype.
+This can help overcome the problem of losing informations in the feature extraction process but
+			arises another problem. In fact, it is not clear how the features should be weighted when combined. \\
+			About the machine learning feature extraction, the biggest limitation is human interpretability.
+In fact, there is still no way to clearly interpret the features extracted by a machine learning system, since
+			these are in form of arrays of numbers. \\
+			The biggest limitations come with the alternative method.
+This method can have two possible approaches, and one of them is asking people to list a set of features and using them to build the prototype.
+This
+			method is a big limitation since, as will be explained later, it is not clear how these features should be used in prototype construction.
 
@@
 				\begin{subfigure}[!t]{0.48\linewidth}
-					\centerline{\includegraphics[height=0.4\textheight]{imgs/swallow_2_edges.jpg}}
+					\centerline{\includegraphics[width=0.4\linewidth]{imgs/swallow_2_edges.jpg}}
 				\end{subfigure}

### 2022-06-24 paper.tex
Finished for resubmission

@@
 
-			\noindent Typicality is one of the key concepts that will be used in this paper, so it is fundamental that it is defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
+			\noindent Typicality is one of the key concepts that will be used in this paper, so it is fundamental that it is defined. In a paper by Dieciuc and Folstein \cite{dieciuc2019typicality},
 			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
@@
 			\noindent Prototypes are another key concept used in this paper and, as the concept of typicality, should be defined. In this case, there are some differences based on the field that it is 
-			examined. According to Murphy's Big Book of Concepts\cite{Murphy:2002}, a prototype is the best example of a category, which corresponds to the most typical item. In this case 
+			examined. According to Murphy's Big Book of Concepts \cite{Murphy:2002}, a prototype is the best example of a category, which corresponds to the most typical item. In this case 
 			it is specified that this item may not be something that exists physically, but it is an average of what people see from real world examples. Adopting the example that the 
@@
 
-					One of the first feature extraction methods implemented in image processing is edge detection.				
-					In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
-					These are usually divided into two groups, gradient-based and Gaussian-based. 
-					Some examples are the Sobel operator and the Canny edge detector. 
-					Each algorithm has its own peculiarities and it is the user's job to find 
-					the most appropriate for its goal~\cite{owotogbe2019edge}.\\
-
 					\begin{figure*}[!ht]
@@
 					\end{figure*}
+
+					One of the first feature extraction methods implemented in image processing is edge detection.				
+					In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
+					These are usually divided into two groups, gradient-based and Gaussian-based. 
+					Some examples are the Sobel operator and the Canny edge detector. 
+					Each algorithm has its own peculiarities and it is the user's job to find 
+					the most appropriate for its goal \cite{owotogbe2019edge}.
+					An example of the result of this process is in Figure \ref{fig:1}.\\
 
@@
 					A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
-					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{felzenszwalb2005representation}.
+					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes \cite{felzenszwalb2005representation}.
 For the goal of the experiment proposed here, some deformable shape
@@
 					After the classic techniques, machine learning began to be involved in feature extraction. In particular there are some papers that explain the results achieved with machine learning.\\
-					\noindent In 2019, a paper written by Varshni et al. that proposes a method~\cite{varshni2019pneumonia} to classify images using CNNs, trying to understand if a patient 
+					\noindent In 2019, a paper written by Varshni et al. that proposes a method \cite{varshni2019pneumonia} to classify images using CNNs, trying to understand if a patient 
 					has pneumonia or not. After the preprocessing, there is the feature extraction process. For this step, the authors used different pretrained models.
@@
 					\noindent In 2019, Guamei et al.
-wrote a paper about hybrid feature extraction methods to classify brain tumours~\cite{gumaei2019hybrid}.
+wrote a paper about hybrid feature extraction methods to classify brain tumours \cite{gumaei2019hybrid}.
 The process described in the paper is divided into three points.
@@
 The techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent
-					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it is probably more meaningful to use normal 
+					networks, as seen in a paper by Hu et al. \cite{hu2020spatial} and in a paper by Rasti et al. \cite{rasti2020feature}. For the reasons just said, it is probably more meaningful to use normal 
 					images than these ones.
@@
 					CNNs are mostly used to deal with images.\\
-					In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs~\cite{wu2017introduction}.
+					In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs \cite{wu2017introduction}.
 These networks use mostly three kind of layers: Dense layers (which are fully connected layers),
@@
 This is not the first time that siamese networks are used for image matching, as shown in a paper written in 2016 by
-					Melekhov et al.~\cite{melekhov2016siamese}, but with a little difference in the objective of the matching.
+					Melekhov et al.
+\cite{melekhov2016siamese}, but with a little difference in the objective of the matching.
 The objective of the paper was to learn a general similarity for image retrieval, while on the case of this
@@
 
-				\noindent In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017~\cite{appalaraju2017image}.
+				\noindent In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017 \cite{appalaraju2017image}.
 In this work they explore the possibility to
@@
 One of them is healthcare, as shown in a paper by Suo et al., written in
-				2017, that introduces a model used to make personalized prediction of diseases for patients, basing the prediction on a similarity related method, learned using CNNs~\cite{8217759}.
+				2017, that introduces a model used to make personalized prediction of diseases for patients, basing the prediction on a similarity related method, learned using CNNs \cite{8217759}.
 In this paper, before
@@
 In this work, the authors used a siamese architecture to learn a similarity metric and applied it
-				in the field of face verification~\cite{chopra2005learning}.\\
+				in the field of face verification \cite{chopra2005learning}.\\
 				More interestingly, there are also other papers, in particular a paper by Attarian et al. written in 2020 uses $VGG16$. This paper's goal is to use this CNN to predict human similarity 
-				judgments~\cite{attarian2020transforming}. Using $VGG16$, the authors were able to achieve good results, with over 90\% in validation accuracy.
+				judgments \cite{attarian2020transforming}. Using $VGG16$, the authors were able to achieve good results, with over 90\% in validation accuracy.
 
@@
 The ranking, as the rating described in \ref{sec:typval}, cannot be performed on all images of the dataset,
-			so it's necessary to split the ranking and rank the images in different forms and then use the informations coming from different subjects and infer the informations about typicality from these answers.
+			so it is necessary to split the ranking and rank the images in different forms and then use the informations coming from different subjects and infer the informations about typicality from these answers.
 
@@
 
-		\subsection{Considerations about the survey\lable{sec:cas}}
+		\subsection{Considerations about the survey\label{sec:cas}}
 
@@
 				than in the ranking method, since a higher position on the list corresponds to a higher typicality. 
-				Another positive aspect of this method is that if a person did not think of a particular example, it won't appear on the ratings. This fact can help identifying the real typicality 
+				Another positive aspect of this method is that if a person did not think of a particular example, it will not appear on the ratings. This fact can help identifying the real typicality 
 				without the possible bias introduced by presenting to a subject an image of an example that did not come to mind.
@@
 				ducks and swans in the category ``bird'', these examples will not appear on the list. Although this technique presents a lower bias, it results in a great difficulty in prototype construction.
-
-			\subsubsection{Considerations on how to choose}
+				\vspace{12pt}
 
@@
 
-		\subsection{Considerations about prototype construction\label{sec:cpc}}
+		\subsection{Considerations and difficulties on prototype construction\label{sec:cpc}}
 
@@
 			of numerical values, that are not easily interpretable. As of 2022, there has been some research on the topic of interpretability and explainability of machine learning, like for example 
-			a work by Carvalho written in 2019~\cite{electronics8080832}, 
+			a work by Carvalho written in 2019 \cite{electronics8080832}, 
 			but the field is still growing, also given the interest deriving from the AI-Act, the proposition of the European Union in the field of artificial intelligence.
@@
 The growing interest produced some results, but still they are not enough to easily interpret machine learning
-			features.\\
-			Most likely, in the future will be possible to look at the features extracted by a neural network and comprehend their meaning.
-When this will be possible, independently of the feature extraction techniques
+			features.
+In particular, there are some interesting works regarding computer vision.
+Mahendran and Vedaldi, for example, explores image inversion techniques to understand to which extent it is possible to
+			reconstruct the image itself \cite{mahendran2015understanding}. In 2018, Lempitsky, Vedaldi and Ulyanov wrote a paper that shows how a randomly initialized network can be used to invert 
+			deep neural representations \cite{8579082}.\\
+			Most likely, especially considering the papers on image inversion,
+			in the future will be possible to look at the features extracted by a neural network and comprehend their meaning. When this will be possible, independently of the feature extraction techniques 
 			used, the human interpretability will be possible, and with that in mind it would be probably more convenient to extract the features using neural networks. The reason behind this consideration is 
@@
 				\begin{subfigure}[!t]{0.48\linewidth}
-					\centerline{\includegraphics[width=0.4\linewidth]{imgs/swallow_2_edges.jpg}}
+					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_2_edges.jpg}}
 				\end{subfigure}
-				\caption{Edge extraction of different swifts}
+				\caption{Edge extraction of swifts in different poses}
 				\label{fig:9}
